% Run only with XeLaTeX!
%---------------------------------------------------------------------
%	FORMATING AND TYPESETTING
%---------------------------------------------------------------------

% Set document class
\documentclass[12pt,a4paper]{article}

% Option to change margin size
\usepackage[margin=2cm]{geometry}

% Font and encoding settings
\usepackage[T1]{fontenc}
%\usepackage[utf8]{inputenc} not necessary with xelatex?
\usepackage{yfonts} % germanic fonts (fraktur...)
%\defaultfontfeatures{Ligatures=TeX} %??

% Footnotes
\usepackage[stable]{footmisc}

% Indentation and spacing
\usepackage{indentfirst} % indentation
\usepackage{enumitem}[leftmargin=0pt] % spacing
\setlist{nosep}

% Multi column environment
\usepackage{multicol}

% Formating of titles
\usepackage{titlesec}
\titleformat{\section}
{\normalfont\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}
{\normalfont\normalsize\bfseries}{\thesubsection}{1em}{}
\titleformat{\subsubsection}
{\normalfont\small\bfseries}{\thesubsubsection}{1em}{}
\titleformat{\paragraph}[runin]
{\normalfont\small\bfseries}{\theparagraph}{1em}{}
\titleformat{\subparagraph}[runin]
{\normalfont\small\bfseries}{\thesubparagraph}{1em}{}
\usepackage[titletoc]{appendix}

% Math typesetting packages
\usepackage{amsmath, amssymb, amsthm, mathtools, commath}
\usepackage[warnings-off={mathtools-colon,mathtools-overbracket}]{unicode-math} % makes \mathbb{1} work and changes font of mathbb
\usepackage[mathscr]{euscript} % euler script font
\usepackage{tikz-cd} % tikz commutative diagrams
\usepackage{thmtools, thm-restate} % theorem tools, especially restatable

\AtBeginDocument{\renewcommand\setminus{\smallsetminus}} % \setminus doesn't work in unicode-math 

%---------------------------------------------------------------------


%---------------------------------------------------------------------
%	GRAPHICS
%---------------------------------------------------------------------

\usepackage{float}
\usepackage{caption}
\usepackage{graphicx}
\graphicspath{{images/}}

\usepackage{pdfpages} % for inserting pdf pages


%---------------------------------------------------------------------


%---------------------------------------------------------------------
%	BIBLIOGRAPHY
%---------------------------------------------------------------------

\usepackage[backend=biber,style=alphabetic]{biblatex}
\renewcommand*{\bibfont}{\small}
\addbibresource{text.bib}

%---------------------------------------------------------------------


%---------------------------------------------------------------------
%	HYPERLINKS
%---------------------------------------------------------------------

% Define the colors
\usepackage{xcolor}
\definecolor{brown}{HTML}{CD853F}
\definecolor{blue}{HTML}{4169E1}
\definecolor{green}{HTML}{2E8B57}

% Setup options for hyperlinks
\usepackage{hyperref}
\hypersetup{
colorlinks=true, linkcolor=black, breaklinks=true,
linktoc=all, bookmarksnumbered=true,
urlcolor=brown, linkcolor=blue, citecolor=green, % Link colors
}

% Referencing package
\usepackage{cleveref}
\crefname{section}{\S\!}{\S\S\!}
\Crefname{section}{\S\!}{\S\S\!}


%---------------------------------------------------------------------
%	THEOREM STYLES
%---------------------------------------------------------------------

% Define a dummy counter to keep count for all sub-environments
\newcounter{counter} \numberwithin{counter}{section}

% Define theorem styles here based on the definition style
\theoremstyle{definition}
\newtheorem{definition}[counter]{Definition}
\newtheorem{construction}[counter]{Construction}
\newtheorem{observation}[counter]{Observation}

% Define theorem styles here based on the plain style
\theoremstyle{plain} 
\newtheorem{theorem}[counter]{Theorem}
\newtheorem*{theorem*}{Theorem}
\newtheorem{corollary}[counter]{Corollary}
\newtheorem{lemma}[counter]{Lemma}
\newtheorem{proposition}[counter]{Proposition}
\newtheorem*{proposition*}{Proposition}
\newtheorem{conjecture}[counter]{Conjecture}


% Define theorem styles here based on the remark style
\theoremstyle{remark}
\newtheorem{example}[counter]{Example}
\newtheorem{remark}[counter]{Remark}


%---------------------------------------------------------------------


%---------------------------------------------------------------------
%	NEW COMMANDS
%---------------------------------------------------------------------

% general target category
\newcommand{\catC}{\mathscr{C}}

% categories of factorization algebras
\newcommand{\falg}{\mathscr{F} \mathsf{Alg}}
\newcommand{\lcfa}{\mathscr{F} \mathsf{Alg}^{\mathsf{lc}}}

% category of manifolds
\newcommand{\mfld}[1][s]{%
    \ifx r#1\mathsf{Mfld}\else
    \ifx s#1\mathscr{M} \mathsf{fld}\else
    \mathrm{Illegal~option}%
    \fi\fi
}

% category of disks
\newcommand{\disk}[1][s]{%
    \ifx r#1\mathsf{Disk}\else
    \ifx s#1\mathscr{D} \mathsf{isk}\else
    \mathrm{Illegal~option}%
    \fi\fi
}

% category of opens
\newcommand{\opens}[1][s]{%
    \ifx r#1\mathsf{Opns}\else
    \ifx s#1\mathscr{O} \mathsf{pns}\else
    \mathrm{Illegal~option}%
    \fi\fi
}

% category of cosheaves
\newcommand{\csheaves}[1][n]{%
    \ifx n#1 \mathsf{c} \mathscr{S} \mathsf{hv}\else
    \mathsf{c} \mathscr{S} \mathsf{hv}^{\mathsf{#1}}
    \fi
}

% category of infinity categories
\newcommand{\cat}{\mathscr{C} \mathsf{at}_{\infty}}

% template for category of algebras
\newcommand{\alg}[1]{\mathscr{A} \mathsf{lg}_{#1}}

% template for category of locally constant algebras
\newcommand{\lcalg}[1]{\mathscr{A} \mathsf{lg}^{\mathsf{lc}}_{#1}}

% half-open interval
\newcommand{\hoint}{\mathbb{R}_{\geq 0}}

% Cech complex
\newcommand{\cech}{\check{\mathsf{C}}}

% Category of basics
\newcommand{\bsc}{\mathscr{B} \mathsf{sc}}
\newcommand{\bstr}{\mathscr{B}}

% Open cone
\newcommand{\cone}[1][n]{%
    \ifx b#1\overline{\mathsf{C}}\else
    \ifx n#1\mathsf{C}\else
    \mathrm{Illegal~option}%
    \fi\fi
}


%---------------------------------------------------------------------

%\usepackage{subfiles}

\setcounter{section}{-1}

\begin{document}

% Set title, author and date
\title{Factorization Algebras and Factorization Homology on Stratified Spaces}
\author{Aleksandar Ivanov, Ödül Tetik}
\date{}
\maketitle

\begin{abstract}
    We endeavor to fully describe (locally constant) factorization algebras on stratified spaces, by giving a description of the $\infty$-operad that underlies them through the use of factorization homology. We also give a result about a collar-gluing property that the $\infty$-categories of (locally constant) factorization algebras satisfy, which enables novel descriptions of these on more complicated spaces. Finally, we outline a classification scheme for locally constant factorization algebras on some stratified manifolds. Parts of this work were adapted from a Master's thesis dissertation submitted to ETH Z\"urich for the first author.
\end{abstract}

\tableofcontents





\section{Introduction}

{\color{red} Needs to be rewritten slightly when we finalize decision on what to include.}

In this work we will explore the concepts of factorization algebras and factorization homology over stratified spaces. These two concepts, which at first sight will looks very different, will turn out to be closely related. We will strive to keep the discussion at the level of stratified spaces, while making a comparison to results in the smooth case. Some results we will meet have been proven in the smooth case, but with methods which do not (at the present moment) generalize to the stratified case. We will endeavor to point these out and give proofs that hold more generally. The outline of the text is as follows:

%\textbf{\Cref{ch:strat_spaces} Stratified Spaces:} The first section deals with setting up the theory of stratified spaces that we will use. It is essentially a recap of the necessary results from the work of Ayala, Francis and Tanaka (AFT) \cite{aft_localstrut}, which is one of our main sources. The idea and fundamentals of stratified spaces have existed for a long time in different incarnation beginning with the work of Whitney \cite{whitney92}. The reason why we choose to work with this particular version of stratified spaces is due to them supporting a notion of conical smoothness that is a generalization of smoothness of manifolds. Furthermore, the theory of factorization homology has been developed with these spaces in mind, which eases the process of extending certain results to the stratified case much easier. We will not go into the full details that this incarnation of the theory has to offer, but instead we will only mention results that we will make use of later on. Beyond conical smoothness, this will include tangential structure and its stratified generalization, together with the packaging of both of these data into the concept of an $\infty$-category of basic singularity types. For the proofs of these statements the reader is encouraged to consult \cite{aft_localstrut}.

%\textbf{\Cref{ch:fact_hom} Factorization Homology:} The second section will present the theory of factorization homology. Similar to the first section this will mostly be a recap of useful results developed by Ayala, Francis and Tanaka. Specifically, the stratified space results can be found in \cite{aft_fhstrat}, while the results for topological manifolds can be found in \cite{af_fhtop}. For the purposes of the theory we will need the concept of (structured) disk algebras, since this will be the algebraic input. Factorization homology will then combine this with the data of a specific kind of (possibly stratified) manifold into an object that can be viewed either as an invariant of the manifold or an invariant of the algebra. We will explore the key example of factorization homology over the closed, oriented interval $[-1,1]$, and see how this gives rise to the algebraic concept of the two-sided bar construction. More generally, this underpins the theory because it codifies the property of $\otimes$-excision. Finally, we will also state a classification result \cite[prop.4.8]{aft_fhstrat} about a certain type of disk algebras with stratified structure.

\textbf{\Cref{ch:fact_alg} Factorization Algebras:} The third section introduces the concept of factorization algebras, together with its different variations, like prefactorization algebras and locally constant factorization algebras. Of these, the locally constant factorization algebras will be the ones that capture the different possible stratified structures that a manifold can have, and they will be a large focus of this work. The definitions of these will not be novel. They can be found in the works \cite{cg2016}, \cite{ginot2015} and even \cite{af_primer}. In fact, in the slightly different context of vertex algebras the idea can be traced back to \cite{bd2004}. However, all of the above works take a slightly different perspective in their presentation of the definitions, which we hope to unite in this work. The key result of this section is the following:
%
\begin{theorem*}[\ref{thm:disk_alg=lcfa}]
    There is an equivalence of $\infty$-categories between locally constant factorization algebras over a stratified manifold $M$ and $\disk_{/M}$-algebras
    %
    \begin{equation}
        \int: \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_M (\catC),
    \end{equation}
    %
    given by factorization homology,
\end{theorem*}
%
as well as its \Cref{cor:disk_alg=falg} for the case of ordinary factorization algebras. These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case). We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as state a result for locally constant factorization algebras on product spaces, which confirms a conjecture of \cite{ginot2015}:
%
\begin{proposition*}[\ref{prop:exp_of_products_lc}]
    Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)).
    \end{equation}
\end{proposition*}
%
Finally, we will examine some examples of factorization algebras whose construction is known, specifically, locally constant factorization algebras on the intervals $(-1,1)$, $[-1,1)$ and $[-1,1]$ as well as Euclidean spaces $\mathbb{R}^n$ more generally.

\textbf{\Cref{ch:gluing_disk_alg} Collar-gluings and Disk Algebras:} The fourth section presents a novel result about the behavior of certain types of factorization algebras under the operation of collar-gluing in the manifold variable. It essentially shows that we can reproduce factorization algebras on a stratified manifold if we know them on some particular pieces of it together with the data of how to glue them. Formally, we have
%
\begin{theorem*}[\ref{thm:gluing_lcfas}]
    Given a collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$, the $\infty$-category of locally constant factorization algebras is equivalent to the pullback of $\infty$-categories
    %
    \begin{equation}
        \lcfa_{M} (\catC) \simeq \lcfa_{M_-} (\catC) \bigtimes_{\lcfa{M_0 \times \mathbb{R}} (\catC)} \\cfa_{M_+} (\catC).
    \end{equation}
\end{theorem*}
%
The results of the previous section a very important in the proof of this statement, because we heavily use the properties of factorization homology. A similar version holds for ordinary factorization algebras in the for of \Cref{cor:disk_alg=falg}. This result hugely expands the number of manifolds for which the $\infty$-category of locally constant factorization algebras can be specified. As a straightforward example, it gives a way to work on, and classify, factorization algebras on all higher spheres $S^n$. Without it, only the circle has been described to date (\cite{ginot2015}) using equivariant factorization algebras and inheritance from covering spaces.

\textbf{\Cref{ch:classif_defect_mfld} Classifying $\lcfa$s on Defect Manifolds:} The fifth section focuses on the stratified structure and gives a way to express what effect this has on the locally constant factorization algebras. Specifically, we look at the data of a smooth manifold $M$ with a distinguished, properly embedded submanifold $\Sigma$ (also known as a defect submanifold) as the data of a stratified manifold $M_\Sigma$. We will show that, along with giving algebras associated to the different pieces, locally constant factorization algebras on these manifolds, in some (precise) sense, also encode a module structure associated with $\Sigma$.

\textbf{Further Questions:} The exploration below naturally leads to questions that are beyond the scope of this work. As we will see, factorization algebras only need a topological space to be defined, but locally constant factorization algebras also capture information about the stratified structure. Neither of these, however, capture information about the tangential structure of the manifold, so the question arises:
%
\begin{itemize}
    \item Does there exist a version of factorization algebras that usefully capture information both about the stratified structure of a manifold and about its tangential structure?
\end{itemize}
%
The recent thesis \cite{pena2022} could provide a fruitful direction of exploration of the former concept. In a similar vein, \cite{cg2016} explain why it's important to have the concept of a $G$-equivariant factorization algebra, where $G$ is a Lie group. In particular, according to them, this asks for some definition of a smooth action of $G$ on factorization algebras.
%
\begin{itemize}
    \item Is there a suitable way to encompass this notion in the formalism presented here?
\end{itemize}
%
The beginnings of examining this idea can already be found in the thesis \cite{murray2020}, however the development there, while important, is still preliminary.


\subsection{Conventions on \texorpdfstring{$\infty$}{infinity}-categories}

The $\infty$-categories in this work will use the quasi-category model of $\infty$-category theory introduced by Joyal in \cite{joyal}, which is based on the simplicial sets introduced by \cite{bv73}. The work by Lurie in \cite{lurie_htt} and \cite{lurie_ha} greatly builds on this theory, and questions about fundamental objects or constructions that are in this text will always be answered in those references. This choice is because a great deal of the theory of factorization homology, as well as factorization algebras deal with $\infty$-categories of functors, which are most easily defined for quasi-categories.

It is also important to note that we will not be making a notational distinction between topological categories, Kan enriched categories and $\infty$-categories because of the functors
%
\begin{equation}
    \{ \mathsf{Top}\mathrm{-categories}\} \xrightarrow{\mathsf{Sing}} \{ \mathsf{Kan}\mathrm{-categories}\} \xrightarrow{\mathsf{N}} \cat,
\end{equation}
%
which are both Quillen--equivalences in appropriate ways (\cite{joyal2007quasi,bergner2010survey}). In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself. Similarly, we will not distinguish between (topological) multicategories and their $\infty$-operadic nerve.


\subsection{Stratified Spaces}\label{ssec:strat_spaces}

The spaces that this work will be set in will very often be stratified spaces. Thus, we first need to define what we mean by this concept. There are multiple definitions of stratified spaces in the literature, all of which have their advantages and disadvantages. For our purposes, we will follow the account of \cite{aft_localstrut}. A compatible source is also \cite[sec.A.5]{lurie_ha}. The majority of the work on factorization homology has so far been elaborated using this particular set of definitions, and similarly the stratified spaces used in the literature on factorization algebras are usually subsumed too. Further details are, of course, discussed in the original \cite{aft_localstrut}, where one can find great explanations of the definitions that are needed, and detailed proofs of the theorems that can be proven.


\subsection{Factorization Homology}\label{ssec:fact_hom}

Factorization homology (also known as topological chiral homology) is a construction that to the data of a smooth manifold $M$ and an algebra $A$ valued in a symmetric monoidal $\infty$-category $\catC$ assigns an object
%
\begin{equation}
    \int_{M} A \in \catC.
\end{equation}
%
The physical interpretation is that given a spacetime $M$ and local observables $A$, $\int_MA$ returns global observables, though typically not all of them.

This implementation, with $M$ relaxed to a stratified manifold and $A$ to an appropriate type of algebra, is sometimes termed `alpha' factorization homology, as opposed to the `beta' version of \cite{ayala2020factorization} that evaluates $(\infty,n)$-categories on variframed stratified $n$-manifolds. In this work, we will be concerned, in this sense, with alpha factorization homology. 

Fixing the algebra, the construction is functorial with respect to open embeddings in the manifold variable, which is the starting point to show that it is a chain level homology theory in a generalized sense. The initial chiral version was first introduced in \cite{bd2004}, and a topological version was introduced by \cite{lurie_ha}. The theory of factorization homology in the manner that we will recall here has been developed in \cite{francis2013,af_fhtop, aft_fhstrat}. We will also follow the introductory text \cite{af_primer}.

In the entirety of this work, we fix our target $\catC$ to be a symmetric monoidal $\infty$-category that is \emph{$\otimes$-presentable} \cite{af_fhtop}, i.e. it satisfies:
%
\begin{enumerate}
    \item $\catC$ is presentable: it admits colimits, and every object is a filtered colimit of compact objects, and
    \item the monoidal structure distributes over colimits: for all $c \in \catC$, the functor $c \otimes -: \catC \xrightarrow{} \catC$ takes colimit diagrams to colimit diagrams.
\end{enumerate}

\begin{remark}\label{rem:inherit_sym_mon_struct}
    For developing the theory of factorization homology the assumption that $\catC$ has all \emph{sifted} colimits, and that the monoidal structure commutes with these, is enough. However, if we want the $\infty$-category of algebras valued in $\catC$ to inherit the properties of having sifted colimits that commute with the monoidal structure, then we must require that $\catC$ has \emph{all} (small) colimits. This will similarly be the case for factorization algebras. The stronger requirement also doesn't exclude any of the core examples that we are interested in.
\end{remark}

\begin{example}
    The following are examples of $\otimes$-presentable categories:
    %
    \begin{enumerate}
        \item chain complexes $\mathscr{C}\mathsf{h}_{\mathbb{k}}$ over a commutative ring $\mathbb{k}$, where equivalences are given by quasi-isomorphism. The symmetric monoidal structure can be both direct sum $\oplus$ or tensor product $\otimes$.
        \item Any cocomplete, Cartesian closed $\infty$-category together with categorical product. (for example $\mathsf{Spaces}$ or $\cat$).
    \end{enumerate}
    %
    In particular, $(\mathscr{C}\mathsf{h}_{\mathbb{k}}, \otimes)$ is the most relevant for physical examples which is why it is the target of choice in \cite{cg2016} and \cite{ginot2015}.
\end{example}

We also fix an $\infty$-category of basics $\bstr \xrightarrow{} \bsc$.

\begin{remark}\label{rem:disk_b=disk_bsc}
    Since we will be dealing with the relative case for the majority of the work, and because $\disk(\bstr)_{/M}$ (and the related slice $\infty$-operads) does not actually depend on the particular tangential structure, as long as $M$ admits it, we will simplify our notation down to $\disk_{/M}$.
\end{remark}

\begin{remark}\label{rem:fin_equiv_natural}
    A few times in this work we will encounter the fact that a final functor $F: \mathscr{A} \xrightarrow{} \mathscr{B}$ between $\infty$-categories induces an equivalence
    %
    \begin{equation}\label{eq:fin_equivs_obj}
        \mathsf{colim}(G) \xrightarrow{\ \ \simeq \ \ } \mathsf{colim}(G \circ F),
    \end{equation}
    %
    for each functor $G: \mathscr{B} \xrightarrow{} \mathscr{C}$, whenever both colimits exist. We remark here that these equivalences are actually even natural in $G$. To explain this, we first notice that the equivalences in \Cref{eq:fin_equivs_obj} actually arise from equivalences between $\infty$-categories
    %
    \begin{equation}\label{eq:fin_equivs_cat}
        \mathscr{C}_{G/} \xrightarrow{\ \ \simeq \ \ } \mathscr{C}_{G \circ F /},
    \end{equation}
    %
    as discussed in \cite[prop.4.1.1.8]{lurie_htt}, where the functor is the obvious one. Furthermore, \cite[\href{https://kerodon.net/tag/016H}{016H}]{lurie_kerodon} tells us that the slice construction is functorial, which, after restricting, defines the functors
    %
    \begin{align}
        &S: \mathsf{Fun}(\mathscr{B}, \mathscr{C}) \xrightarrow{\ \ \ } \cat& \mathrm{and}& &S': \mathsf{Fun}(\mathscr{A}, \mathscr{C}) \xrightarrow{\ \ \ } \cat,&
    \end{align}
    %
    whose value on objects is given by $G \mapsto \mathscr{C}_{G/}$. We can now state that by naturality in $G$ we mean that the functors of \Cref{eq:fin_equivs_cat} assemble into an equivalence of functors   
    %
    \begin{equation}
        S \xrightarrow{\ \ \simeq \ \ } S' \circ F^*
    \end{equation}
    %
    in $\mathsf{Fun}(\mathsf{Fun(\mathscr{B}, \mathscr{C})}, \cat)$. But this is obviously the case, given the description of the maps in \Cref{eq:fin_equivs_cat}, and amounts to nothing more than bookkeeping.
\end{remark}

In particular, the above remark slightly extends \cite[prop.2.34]{aft_fhstrat}, as well as \cite[thm.2.25]{aft_fhstrat}, which become:
%
\begin{proposition}[{\cite[thm.2.34]{aft_fhstrat}}]\label{prop:barconst=intinterval}
    There is an equivalence of functors between the two-sided bar construction
    %
    \begin{equation}
        \mathsf{B}: \alg{\mathsf{Assoc^{RL}}}(\catC) \xrightarrow{} \catC
    \end{equation}
    %
    and factorization homology over the oriented closed interval
    %
    \begin{equation}
        \int_{[-1,1]}: \alg{\mathsf{Assoc^{RL}}}(\catC)\simeq \alg{\disk_{/[-1,1]}} (\catC) \xrightarrow{\ \int \ } \alg{\mfld_{/[-1,1]}} (\catC) \xrightarrow{\ \mathsf{ev}_{[-1,1]} \ } \catC.
    \end{equation}
    %
    In particular, given a unital, (homotopy) associative algebra $A$, a unital right $A$-module $R$ and a unital left $A$-module $L$, there is an equivalence of objects
    %
    \begin{equation}
        \int_{[-1,1]} (R, A, L) \xrightarrow{\ \ \simeq \ \ } R \bigotimes\limits_{A} L.
    \end{equation}
\end{proposition}

\begin{proposition}[{\cite[thm.2.25]{aft_fhstrat}}]\label{prop:fh_pushforward}
    Let $f: M \xrightarrow{} N$ be a weakly constructible bundle. There is a pushforward functor
    %
    \begin{equation}
        f_*: \alg{\disk_{/M}}(\catC) \xrightarrow{\quad} \alg{\disk_{/N}}(\catC).
    \end{equation}
    %
    This functor is such that there is a canonical equivalence between functors
    %
    \begin{equation}
        \int_M -, \int_N f_* - : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \catC.
    \end{equation}
\end{proposition}






\section{Factorization Algebras}\label{ch:fact_alg}

\subsection{Definition of Factorization Algebras}

Factorization algebras are a rigorous way to capture the idea of assigning an object to each piece of a space, together with a local-to-global principle that allows one to find out about larger pieces from smaller ones. The first ideas around factorization algebras were introduced by \cite{bd2004} in the context of vertex algebras in CFTs. These were geometric in nature. The topological version that we present was then introduced by Lurie and subsequently further developed in \cite{cg2016}, especially for the purposes of mathematical physics.

Here we will present these ideas following \cite{cg2016} and \cite{ginot2015} while also trying to express them more categorically in the style of \cite{af_primer}. In this sense, the present work bridges a gap in how factorization algebras are usually presented. 

\begin{definition}
    Let $X$ be a topological space. We regard $\opens[s](X)$ as a multicategory (and consequently as an $\infty$-operad) whose objects are the open sets of $X$, and through the assignment of a unique multi-morphism from $\{U_i\}_{i \in I}$ to $U$ if the $U_i$ are pairwise disjoint and if $\bigcup_{i \in I} U_i \subset U$. A \emph{prefactorization algebra $F$ on $X$ with values in $\catC$} is an algebra in $\catC$ over this $\infty$-operad
    %
    \begin{equation}
        F \in \alg{\opens[s](X)}(\catC).
    \end{equation}
\end{definition}

\begin{remark}
    Restricting to the case of (stratified) manifolds we have an alternative notation for the $\infty$-operad $\opens(X)$, namely $\mfld[r]_{/M}$. This makes a connection to the standard notation used around factorization homology, and is something that we'll make use of later.
\end{remark}

\begin{remark}
    Let's unwind the above definition to understand the underlying data needed to define a prefactorization algebra. On the level of objects, for every open set $U$ we need to assign an object $F(U) \in \catC$. On the level of morphisms, given a pairwise disjoint set of opens $\{U_i\}_{i \in I}$ and an open $U$, such that the $U_i$ all lie in $U$ we need to assign a morphism in $\catC$
    %
    \begin{equation}
        \bigotimes_{i \in I} F(U_i) \xrightarrow{F(\{U_i\},U)} F(U).
    \end{equation}
    %
    As the notation suggests and the operadic symmetry condition guarantees, the maps $F(\{U_i\},U)$ only depend on the set of $U_i$ and not on any particular order of the $U_i$, which is also allowed on the left-hand side by the symmetric monoidal structure of $\catC$. Furthermore, the operadic associativity condition imposes that given pairwise disjoint $\{U_i\}_{i \in I}$ that all lie in $U$, and for each $i \in I$, pairwise disjoint $\{ V_{i, j}\}_{j \in J_i}$ that all lie in $U_i$, there is a commutative diagram in $\catC$
    %
    \begin{equation}
        \begin{tikzcd}
            \bigotimes\limits_{(i,j)} F(V_{i,j}) \arrow[rd, shorten <=-2ex, "\bigotimes\limits_{i} F(\{V_{i, j}\} {,} U_i)"'] \arrow[rr, "F( \{V_{i, j}\} {,} U)"] &   & F(U) \\
            & \bigotimes\limits_{i} F(U_i) \arrow[ru, "F( \{U_i \} {,} U)"'] &,          
        \end{tikzcd}
    \end{equation}
    %
    where the $(i,j)$ tensor product runs over all possible pairs $i \in I$ and $j \in J_i$. Finally, the operadic unitarity condition actually tells us that the morphisms $F(\{U\}, U)$ are equivalent to the identity morphism.

    We also get out that an algebra morphism $\phi: F \rightarrow G$ is simply a family of maps $\phi(U): F(U) \rightarrow G(U)$ for each open set $U$, such that it respects the operations of the algebra. Namely, for each multi-morphism $\{ U_i \}_{i \in I} \rightarrow U$ there is a commuting square
    %
    \begin{equation}\label{cd:fa_morphisms}
        \begin{tikzcd}[row sep=large, column sep = large]
            \bigotimes\limits_{i \in I} F(U_i) \arrow[r, "F(\{ U_i\} {,} U)"] \arrow[d, "\bigotimes\limits_{i \in I} \phi(U_i)"'] & F(U) \arrow[d, "\phi(U)"] \\
            \bigotimes\limits_{i \in I} G(U_i) \arrow[r, "G(\{ U_i\} {,} U)"'] & G(U).
        \end{tikzcd}
    \end{equation}

\end{remark}

\begin{remark}\label{rem:op_to_op}
    There is an obvious inclusion functor from the poset $\opens[r](X)$ of open subsets of $X$, ordered by inclusion, to the multicategory $\opens[s](X)$, namely, the one which hits only those multi-morphisms $\{U_i\}_{i \in I} \rightarrow U$, where the cardinality of the finite set $I$ is 1.
\end{remark}

A factorization algebra will be a prefactorization algebra that further satisfies a certain gluing condition that lets us construct its value on `larger' sets if we know it on `smaller' sets. More formally, this will be a kind of cosheaf condition, that we describe now, following \cite{weiss1999,af_primer}.

We endow the poset $\opens[r](X)$ with a Grothendieck topology called the \emph{Weiss} Grothendieck topology \cite{weiss1999}. In this topology a sieve $\mathscr{U} \subset \opens[r](X)_{/U}$ on $U$ is a covering sieve if for each finite subset $S \subset U$, there is an object $(e: V \rightarrow U) \in \mathscr{U}$ for which $S \subset e(V)$. In other words, a family $\{ V_i \rightarrow U\}_{i \in I}$ is a Weiss cover of $U$ if every set of finitely many points in $U$ is contained in some $V_i$. Contrast this with the standard Grothendieck topology on the poset of opens $\opens[r](X)$, in which instead of a finite set we have a one-element set. Thus, every Weiss cover is a cover in the standard sense, but not necessarily the other way around.

\begin{definition}
    The $\infty$-category of \emph{$\catC$-valued Weiss (homotopy) cosheaves on $X$} is the full $\infty$-subcategory
    %
    \begin{equation}
        \csheaves[W]_{X}(\catC) \subset \mathsf{Fun}(\opens[r](X), \catC),
    \end{equation}
    %
    of the $\infty$-category of copresheaves, consisting of those functors $F: \opens[r](X) \rightarrow \catC$ for which, for each Weiss covering sieve $\mathscr{U} \subset \opens[r](X)_{/U}$, the canonical functor
    %
    \begin{equation}
        \mathscr{U}^{\vartriangleright} \rightarrow \opens[r](X)_{/U} \rightarrow \opens[r](X) \xrightarrow{F} \catC,
    \end{equation}
    %
    where $\mathscr{U}^{\vartriangleright} \rightarrow \opens[r](X)_{/U}$ is the functor from the colimit cone that assigns $U$ to the colimit object, is a colimit diagram.
\end{definition}

\begin{remark}
    In other words, $F$ is a Weiss cosheaf if it is a functor that sends colimits (which, in this case, are unions) of Weiss covers $\{ U_i \xhookrightarrow{} U \}_{i \in I}$ to colimits in $\catC$
    %
    \begin{equation}
        F(U) \simeq F \bigg( \bigcup_{i \in I} U_i \bigg) \simeq \mathrm{colim}_{i \in I} F(U_i).
    \end{equation}
\end{remark}

\begin{remark}
    If we're working with the $\infty$-category $\mfld_{/X}$, then we define cosheaves on it through the pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \csheaves[W] (\mfld_{/X}, \catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \mathsf{Fun}(\mfld_{/X}, \catC) \arrow[d] \\
            \csheaves[W] (\mfld_{/X}, \catC) \arrow[r] & \mathsf{Fun}(\mfld_{/X}, \catC).
        \end{tikzcd}
    \end{equation}
\end{remark}

\begin{definition}
    The $\infty$-category of \emph{($\catC$-valued) factorization algebras on $X$}\footnote{These are called homotopy factorization algebras in \cite{cg2016}, however we do not consider the lax version of factorization algebras that they also present.} is the full $\infty$-subcategory of $\alg{\opens[s](X)}$ as in the pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \falg_X (\catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \alg{\opens[s](X)}(\catC) \arrow[d] \\
            \csheaves[W]_X(\catC) \arrow[r] & \mathsf{Fun}(\opens[r](X), \catC).
        \end{tikzcd}
    \end{equation}
\end{definition}

\begin{proof}
    The previous definition implies that the top horizontal functor is fully faithful, which is something we need to prove. The bottom horizontal functor is fully faithful, by the definition of cosheaf, and the right vertical functor forgets the operations with arity higher than $1$. The key observation is that a Weiss cover is pairwise disjoint only when it consists of a single subset. Thus, the cosheaf condition does not affect the algebra morphisms and an equivalence of morphism spaces is trivial to find, namely one is given by the identity map.
\end{proof}

\begin{remark}\label{rem:cech_nerve}
    A factorization algebra is a prefactorization algebra whose restriction to $\opens[r](X)$ is a Weiss cosheaf. This means that the definition can be rewritten in an equivalent way as with all cosheaves. Following \cite{nlab} (which presents the dual case of sheaves) we can express the condition through the \v{C}ech nerve. Let $\mathscr{U}_U = \{ U_i \rightarrow U\}_{i \in I}$ be a (Weiss) cover of an open set $U$ and $F$ be a copresheaf, and define the simplicial object
    %
    \begin{equation}
        \cech_{\bullet}(\mathscr{U}_U, F) := \left( \coprod_{i \in I} F(U_i) \leftleftarrows \coprod_{i, j \in I} F(U_i \cap U_j) \mathrel{\substack{\textstyle\leftarrow\\[-0.6ex]
        \textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow}} \coprod_{i, j, k \in I} F(U_i \cap U_j \cap U_k) \mathrel{\substack{\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow}} \cdots  \right),
    \end{equation}
    %
    where the maps are induced by the value of $F$ on the inclusions of opens. There are canonical maps $F(U_i) \rightarrow F(U)$, so that at the level of simplicial objects there is a canonical map
    %
    \begin{equation}
        \cech_{\bullet} (\mathscr{U}_U, F) \xrightarrow{\quad} F(U)_{\bullet},
    \end{equation}
    %
    to the constant simplicial complex at $F(U)$. Since $\catC$ has (sifted) colimits we can take the geometric realization to obtain a morphism
    %
    \begin{equation}
        \cech(\mathscr{U}_U, F) \xrightarrow{\quad} F(U).
    \end{equation}
    %
    $F$ is a (homotopy) cosheaf if, and only if, this morphism is an equivalence for every open set $U$ and every Weiss cover of it $\mathscr{U}_U$.
\end{remark}

All of our definitions above are valid for all topological spaces, so in particular, also stratified spaces. For the next definition of locally constant factorization algebras though, it will be important to specify more information about the space. In other words, they will capture information about the stratification.

\begin{definition}
    The $\infty$-category of locally constant Weiss cosheaves on a stratified manifold $M$ (or, equivalently, on $\mfld[r]_{/M}$) is the full $\infty$-subcategory
    %
    \begin{equation}
        \csheaves[W, lc]_M (\catC) \subset \csheaves[W]_M (\catC),
    \end{equation}
    %
    of those Weiss cosheaves whose underlying functor $F: \bsc_{/M} \xrightarrow{} \catC$ satisfies
    %
    \begin{equation}
        f(U) \simeq f(V) \Rightarrow F(U) \simeq F(V),
    \end{equation}
    %
    for all $U, V \in \bsc_{/M}$, where $f: \bsc_{/M} \xrightarrow{} \bsc$ denotes the forgetful functor.
\end{definition}

\begin{remark}
    Thus, a functor is locally constant if it takes open embeddings of basics $V \xhookrightarrow{} U$, with equivalent stratifications to equivalences in $\catC$. We emphasize this last point about stratification; the disks have to have equivalent stratifications inherited from the stratified space. In the case of $\hoint$, for example, open embeddings like $(a, b) \rightarrow \left[0, c\right)$, for $0 \leq a < b \leq c$, would \emph{not} be taken to equivalences since the disks have different stratifications.
\end{remark}

\begin{remark}
    Since being locally constant according to the previous definition is only a property of the underlying functor the definition can easily be used to define locally constant prefactorization algebras too.
\end{remark}

\begin{definition}
    The $\infty$-category $\lcfa_M (\catC)$ of \emph{locally constant}\footnote{There is a general definition of locally constant algebra objects in the context of any $\infty$-operad given in \cite[def.2.3.3.20]{lurie_ha}, which, of course, applies here. Our present perspective is more akin to \cite[def.A.1.12]{lurie_ha} whereby we define locally constant cosheaves and then pull this property back to factorization algebras.} \emph{factorization algebras on a stratified manifold $M$ valued in $\catC$} is the full $\infty$-subcategory of $\falg_M (\catC)$ as in the pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \lcfa_M (\catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \falg_M (\catC) \arrow[d] \\
            \csheaves[W, lc]_M (\catC) \arrow[r] & \csheaves[W]_M (\catC).
        \end{tikzcd}
    \end{equation}
\end{definition}

\begin{remark}\label{rem:sym_mon_inheritance}
    As mentioned in \Cref{rem:inherit_sym_mon_struct}, our assumptions on the target $\catC$ allow the $\infty$-categories of factorization algebras of all varieties to acquire a symmetric monoidal structure from the symmetric monoidal structure of $\catC$ pointwise
    %
    \begin{equation}
        (F \otimes G)(U) = F(U) \otimes G(U).
    \end{equation}
    %
    To satisfy the cosheaf condition we use the property that colimits in $\catC$ commute with its symmetric monoidal structure.

    The existence of colimits is also inherited from $\catC$ pointwise through the collection of evaluation functors $\{ \mathsf{ev}_U: \falg_X (\catC) \rightarrow \catC \}$, one for each open $U \subset X$.
\end{remark}



\subsection{The \texorpdfstring{$\infty$-}{infinity }operad of Factorization Algebras}

The way that we have defined the different kinds of factorization algebras only makes clear what the $\infty$-operad governing them is in the case of prefactorization algebras. Limiting our discussion to stratified manifolds, as opposed to general topological spaces, we will show that the $\infty$-operad that governs locally constant factorization algebras can be taken to be $\disk_{/M}$, where we use the notation of \cite{aft_fhstrat}, (which \cite{lurie_ha} alternatively denotes $\mathbb{E}_M^{\otimes}$), and the one that governs ordinary factorization algebras can be taken to be $\disk[r]_{/M}$ (which \cite{lurie_ha} denotes $\mathrm{N}(\mathrm{Disk}(M))^\otimes$). This result is immensely helpful in relating factorization algebras to results in the area of disk algebras. We will see one such example in \Cref{ch:gluing_disk_alg}.

\begin{proposition}\label{prop:fh_disk_to_lcfa}
    Given a stratified manifold $M$, factorization homology provides a functor between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$
    %
    \begin{equation}
        \int : \alg{\disk_M} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC).
    \end{equation}
\end{proposition}

\begin{proof}
    We adopt a proof strategy similar to \cite[prop.3.14]{af_primer}. Unlike there, we work in the relative case of $\disk_{/M}$ instead of $\disk(\bstr)$. Since the $\infty$-category of factorization algebras is defined as a pullback, we will look for a commutative diagram involving $\alg{\disk_{/M}}$, so that, by the universal property of the pullback, we get the stated functor.
    
    We first observe that, by definition, the $\infty$-operad $\opens(M) := \mfld[r]_{/M}$. There are clear functors of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \xhookrightarrow{\ \ \ } \mfld_{/M} \xleftarrow{\ \ \ } \mfld[r]_{/M}.
    \end{equation}
    %
    At the level of algebras over them, they give rise to the commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}
            \alg{\disk_{/M}} (\catC) \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l] \arrow[r] & \mathsf{Fun}(\opens(M), \catC),
        \end{tikzcd}
    \end{equation}
    %
    where the vertical arrows are forgetful functors. Factorization homology as a left Kan extension gives one the adjoints indicated below
    %
    \begin{equation}
        \begin{tikzcd}[row sep = large, column sep = large]
            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC).
        \end{tikzcd}
    \end{equation}
    %
    A result found in \cite[thm.1.2.5]{aft_localstrut} (where they use slightly different notation and call locally constant sheaves constructible) gives us the equivalence
    %
    \begin{equation}
        \csheaves[W](\mfld_{/M}, \catC) \simeq \csheaves[W, lc](\mfld[r]_{/M}, \catC) =: \csheaves[W, lc]_M(\catC),
    \end{equation}
    %
    which at the level of underlying functors, is exactly the restriction along the functor $\opens(M) \xrightarrow{} \mfld_{/M}$, so that we can append this to our commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}[row sep = large, column sep = large]
            \alg{\disk_{/M}} (\catC) \arrow[r, bend left=10, "\int"] \arrow[d] & \alg{\mfld_{/M}} (\catC) \arrow[l, bend left=10] \arrow[r] \arrow[d] & \alg{\opens(M)} (\catC) \arrow[d] \\
            \mathsf{Fun}(\disk_{/M}, \catC) \arrow[r, bend left=10, "\int"] \arrow[dr, dashed] & \mathsf{Fun}(\mfld_{/M}, \catC) \arrow[l, bend left=10] \arrow[r] & \mathsf{Fun}(\opens(M), \catC) \\
            & \csheaves[W](\mfld_{/M}, \catC) \arrow[r, "\simeq"] \arrow[u] & \csheaves[W, lc]_M(\catC) \arrow[u].
        \end{tikzcd}
    \end{equation}
    %
    If we can find the dashed functor which makes the diagram commute, as indicated above, we would be done with the construction. This amounts to showing that the left Kan extension $\int F$ of a functor $F \in \mathsf{Fun}(\disk_{/M}, \catC)$ along $\disk_{/M} \xhookrightarrow{} \mfld_{/M}$ is automatically a Weiss cosheaf. By the definition of $\csheaves[W](\mfld_{/M}, \catC)$, this means that the restriction of $\int F$ to $\mathsf{Fun}(\mfld[r]_{/M}, \catC)$ satisfies the cosheaf property for every Weiss sieve $\mathscr{U} \subset (\mfld[r]_{/M})_{/e}$, where $e:N \xhookrightarrow{} M$ is an open embedding. Here we notice that for the Weiss property to even make sense, we are implicitly using $(\mfld[r]_{/M})_{/(N \xhookrightarrow{} M)} \simeq \mfld[r]_{/N}$.
    
    Since $\catC$ has all relevant colimits the left Kan extension $\int F$ is given pointwise by
    %
    \begin{equation}\label{eq:pointwiseKan}
        \int_e F \simeq \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC),
    \end{equation}
    %
    so what we need to show is that this colimit is equivalent to the colimit
    %
    \begin{equation}\label{eq:cosheaf_colim_relative}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \rightarrow \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    for each covering sieve $\mathscr{U}$. Since we aren't actually trying to get the value of these colimits we can rewrite \Cref{eq:pointwiseKan} into the idiosyncratic form
    %
    \begin{equation}\label{eq:idiosync_form}
        \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    which is easier to compare to \Cref{eq:cosheaf_colim_relative}. Using the fact that $\disk[r]_{/M} \xrightarrow{} \disk_{/M}$ is a final functor, which is a consequence of \cite[prop.2.22]{aft_fhstrat}, and the equivalence $(\disk_{/M})_{/(N \xhookrightarrow{} M)} \simeq \disk_{/N}$ we can rewrite \Cref{eq:idiosync_form} further into
    %
    \begin{align}
        \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC) \\ \simeq \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC).
    \end{align}
    %
    Denoting the functor $\mfld[r]_{/N} \simeq (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC$ by $K_F$ and comparing with \Cref{eq:cosheaf_colim_relative} we need to show
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C) \simeq \mathsf{colim} (\disk[r]_{/N} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C),
    \end{equation}
    %
    but this already follows from part 2 of the proof of \cite[prop.2.22]{af_primer}, and is equivalent to the statement that the functor
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{} \mfld[r] \xrightarrow{\disk_{/-}} \cat) \xrightarrow{} \disk_{/N},
    \end{equation}
    %
    is final.
\end{proof}

\begin{remark}
    Intuitively, the key idea for the statement and proof is that $\disk[r]_{/N}$ is a basis for the Weiss Grothendieck topology on manifolds. This is essentially because for each finite set of points $S \subset N$, and each Weiss cover of it $U_S$, we can take small enough disks $\{ D_s \}_{s \in S}$ around each point, by virtue of $N$ being a manifold, and their disjoint union will cover $S$, as well as satisfy $\sqcup_{s \in S} D_s \subset U_S$. The proof of \cite[prop.2.22]{af_primer} makes this precise, and the above proof transports that idea to the relative case.
\end{remark}

From the proof of \Cref{prop:fh_disk_to_lcfa} it is easy to see that we can make a similar statement for ordinary factorization algebras too:

\begin{corollary}\label{cor:fh_disk_to_falg}
    Given a stratified manifold $M$ factorization homology provides a functor
    %
    \begin{equation}
        \int: \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \ \ } \falg_{M} (\catC).
    \end{equation}
\end{corollary}

\begin{theorem}\label{thm:disk_alg=lcfa}
    For each stratified manifold $M$, the previously constructed factorization homology functor provides an equivalence of $\infty$-categories between $\disk_{/M}$-algebras and locally constant factorization algebras on $M$. Equivalently, the $\infty$-operad governing locally constant factorization algebras can be taken to be $\disk_{/M}$
    %
    \begin{equation}
        \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_M (\catC).
    \end{equation}
\end{theorem}

\begin{proof}
    To show essential surjectivity of $\int$, for each $F \in \lcfa_M (\catC)$ we will find an equivalence $\int F| \simeq F$ in $\lcfa_M (\catC)$, with $F|$ to be defined later. Since $\lcfa_M (\catC) \xrightarrow{} \alg{\opens(M)}$ is fully faithful, this amounts to finding equivalences of prefactorization algebras, namely a family of equivalences
    %
    \begin{equation}
        \int_U F| \xrightarrow[\simeq]{\ \ \phi (U) \ \ } F(U),
    \end{equation}
    %
    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which preserve the multiplicative structure (see \Cref{cd:fa_morphisms}). Since $F$ is a locally constant factorization algebra the functor
    %
    \begin{equation}
        \lcfa_M (\catC) \xrightarrow{} \csheaves[W, lc](\mfld[r]_{/M}, \catC) \simeq \csheaves[W](\mfld_{/M}, \catC) \xrightarrow{} \mathsf{Fun}(\mfld_{/M}, \catC),
    \end{equation}
    %
    which we omit in the notation, allows us to consider $F$ as a functor from $\mfld_{/M}$. Furthermore, since $\disk[r]_{/U}$ is a Weiss sieve we can write
    %
    \begin{align}
        F(U) &\simeq \mathsf{colim} (\disk[r]_{/U} \xrightarrow{} \disk[r]_{/M} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{F} \catC).
    \end{align}
    %
    By consulting the commutative diagram
    % 
    \begin{equation}
        \begin{tikzcd}
            \disk[r]_{/U} \arrow[d] \arrow[r] & \disk_{/U} \arrow[d] & \\
            \disk[r]_{/M} \arrow[d] \arrow[r] & \disk_{/M} \arrow[d] \arrow[r, "F|"] & \catC, \\
            \mfld[r]_{/M} \arrow[r] & \mfld_{/M} \arrow[ru, "F"'] &  
        \end{tikzcd}
    \end{equation}
    %
    and using the fact that $\disk[r]_{/U} \xrightarrow{} \disk_{/U}$ is final (\cite[prop.2.22]{aft_fhstrat}) immediately gives us that
    %
    \begin{equation}
        F(U) \simeq \mathsf{colim} (\disk_{/U} \xrightarrow{} \disk_{/M} \xrightarrow{F|} \catC) =: \int_U F|.
    \end{equation}
    %
    To preserve the multiplicative structure, these equivalences have to be natural, and there also has to be a commutative diagram
    %
    \begin{equation}\label{eq:mult_strut_comm_square}
        \begin{tikzcd}
            \otimes_i \int_{U_i} F| \arrow[r, "\simeq"] \arrow[d, "\otimes_i \phi (U_i)"', "\simeq"] & \int_{\sqcup_i U_i} F| \arrow[d, "\phi (\sqcup_i U_i)", "\simeq"']\\
            \otimes_i F (U_i) \arrow[r, "\simeq"] & F (\sqcup_i U_i),
        \end{tikzcd}
    \end{equation}
    %
    for each collection of disjoint open sets $\{U_i\}$. Naturality is immediate from the construction because, as already used, each inclusion of open subsets $V \xhookrightarrow{} U$ gives a full subcategory inclusion $\disk[r]_{/V} \xhookrightarrow{} \disk[r]_{/U}$. On the other hand, the existence of the commutative diagram is guaranteed by the equivalence
    %
    \begin{equation}
        \disk[r]_{/\sqcup_i U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_i \disk[r]_{/U_i}.
    \end{equation}

    To show full faithfulness we need to find equivalences of morphism spaces
    %
    \begin{equation}
        \mathsf{Hom}_{\alg{\disk_{/M}} (\catC)} (A, B) \simeq \mathsf{Hom}_{\lcfa_M (\catC)} (\int A, \int B),
    \end{equation}
    %
    for each $A, B \in \alg{\disk_{/M}}$. However, since the functors
    %
    \begin{align}
        &\alg{\disk_{/M}} (\catC) \xrightarrow{\mathsf{f.f.}} \alg{\disk[r]_{/M}} (\catC) &\lcfa_M (\catC) \xrightarrow{\mathsf{f.f.}} \alg{\mfld[r]_{/M}} (\catC)
    \end{align}
    %
    are both fully faithful we are reduced to finding equivalences
    %
    \begin{equation}
        \mathsf{Hom}_{\alg{\disk[r]_{/M}} (\catC)} (A, B) \simeq \mathsf{Hom}_{\alg{\mfld[r]_{/M}} (\catC)} (\int A, \int B).
    \end{equation}
    %
    The existence of these is exactly the requirement that factorization homology in the usual sense is fully faithful, which is part of the statement of \cite[lem.2.17]{aft_fhstrat}
\end{proof}

\begin{remark}
    One perspective on this result, provided by \cite[thm.2.43]{aft_fhstrat}, is that the theory of locally constant factorization algebras captures as much information as (generalized) homology theory in the sense of \cite[def.2.37]{aft_fhstrat}.
\end{remark}

As before, the case of ordinary factorization algebras gets a similar statement whose proof goes along the same lines:

\begin{corollary}\label{cor:disk_alg=falg}
    The $\infty$-operad governing factorization algebras on a stratified manifold $M$ can be taken to be $\disk[r]_{/M}$,
    %
    \begin{equation}
        \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \falg_M (\catC).
    \end{equation}
\end{corollary}

\begin{remark}
    A version of \Cref{thm:disk_alg=lcfa} was proven as \cite[thm.6]{gtz2014} in the case of smooth manifolds. The proof there, however, made crucial use of choosing a Riemannian metric on the manifold and constructing geodesically convex neighborhoods. This technique is, at least presently, not extendable to the stratified case, but our proof above subverts the need for it. 
\end{remark}

\begin{remark}
    As noted at the beginning of \Cref{ssec:fact_hom}, the physical interpretation of this version of factorization homology is a way to take a spacetime $M$ and its local observables $A$, and construct \emph{some}, and typically not all, of the global observables. The previous \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} transfer this observation to factorization algebras, which aligns with the observation of \cite{cg2016} that the current version of factorization algebras can only deal with perturbative quantum field theory. 
\end{remark}

The $\infty$-operad $\disk_{/M}$ is, in general, harder to deal with than its symmetric monoidal counterpart $\disk(\bstr)$. The next lemma outlines a certain situation where this is not the case.

\begin{lemma}\label{lem:disk/M_to_disk}
    Let $M$ be a stratified manifold. If we can find an $\infty$-category of basics $\bstr_M$ such that $M$ admits a $\bstr_M$-structure and such that
    %
    \begin{equation}
        \mathsf{Hom}_{\mfld(\bstr_M)} (V, M) \simeq *
    \end{equation}
    %
    for all $V \in \bstr_M$, then there is an equivalence of symmetric monoidal $\infty$-categories
    %
    \begin{equation}
        \mathsf{Env}(\disk_{/M}) \xrightarrow{\ \ \simeq \ \ } \disk(\bstr_M).
    \end{equation}
\end{lemma}

\begin{proof}
    We follow the proof of \cite[cor.2.33]{aft_fhstrat}. Using \Cref{rem:disk_b=disk_bsc}, the forgetful functor from the slice $\infty$-operad, which is a map of $\infty$-operads, is what will provide the equivalence
    %
    \begin{equation}
        \disk_{/M} \simeq \disk(\bstr_M)_{/M} \xrightarrow{\ \ \ \ } \disk(\bstr_M).
    \end{equation}
    %
    This functor is an equivalence on maximal $\infty$-subgroupoids because for any $V \in \disk(\bstr_M)$ the space of morphisms to $M$ is contractible, so, up to equivalence it is unique. Full faithfulness is provided by the fact that the functor on the active $\infty$-subcategories $\disk_{/M} \xrightarrow{} \disk(\bstr_M)$ is a right fibration. 
\end{proof}

The lemma says that for stratified manifolds $M$ that satisfy the conditions, the classification of locally constant factorization algebras on $M$, i.e. algebras over $\disk_{/M}$ simplifies to the classification of $\disk(\bstr_M)$-algebras in the usual sense
%
\begin{equation}
    \lcfa_M (\catC) \simeq \mathsf{Fun}^\otimes (\mathsf{Env}(\disk_{/M}), \catC) \simeq \alg{\disk(\bstr_M)} (\catC).
\end{equation}
%
This is an improvement because $\disk(\bstr_M)$-algebras are easier to work with, one reason being that $\disk(\bstr_M)$ has the benefit of being not just an $\infty$-operad but even a symmetric monoidal $\infty$-category.

The results of \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} can also be seen as lowering the amount of data that is necessary to say that we have defined a factorization algebra on a stratified manifold. There is a similar, but slightly weaker result \cite[ch.7.2]{cg2016}, which nonetheless works for all Hausdorff topological spaces. The main difference between our result and the result of \cite{cg2016} is that, unlike the `factorizing basis' defined there, we don't require our disks to be closed under finite intersections.


\subsection{Operations on Factorization Algebras}

There are a few important operations that we can do with factorization algebras (and the other mentioned variants) that will be important for our considerations.

\begin{proposition}\label{prop:pushforward}
    Given a continuous map $f:X \rightarrow Y$ between topological spaces, there are pushforward functors
    %
    \begin{align}
        &f_*: \alg{\opens[s](X)} \xrightarrow{\quad} \alg{\opens[s](Y)} &f_*: \falg_X \xrightarrow{\quad} \falg_Y,
    \end{align}
    %
    which, on objects, are given by the prescription
    %
    \begin{equation}
        f_*F (U) := F(f^{-1}U).
    \end{equation}
\end{proposition}

\begin{proof}
    By the definition of continuity, the case of prefactorization algebras is trivial. Thus, the only thing we are left to show is that if $F$ satisfies the Weiss cosheaf property then so does $f_* F$. Given a Weiss cover $\{U_i \xhookrightarrow{} U\}_{i \in I}$ of $U$, we observe that $\{f^{-1}U_i \xhookrightarrow{} f^{-1}U\}_{i \in I}$ is a Weiss cover of $f^{-1}U$. Namely, if $S \subset f^{-1}U$ is a finite subset of $U$, then $f(S)$ is contained in some $U_i$ by the Weiss cover property of $\{U_i \xhookrightarrow{} U\}_{i \in I}$. But in that case $S$ has to be contained in $f^{-1}U_i$, giving it the Weiss cover property too. Thus, by the definition of the pushforward on objects the Weiss cosheaf property is preserved.
\end{proof}

The case of locally constant factorization algebras is different when it comes to the pushforward. This is because it's not immediate that local constancy is preserved when pushed forward. However, if we limit the types of maps we pushforward with we can still construct a functor. The following two results give the flavor of what is required.

\begin{proposition}[{\cite[prop.15]{ginot2015}}]
    If $f: X \rightarrow Y$ is a locally trivial fibration between smooth manifolds then the pushforward functor exists even between the $\infty$-categories of locally constant factorization algebras
    %
    \begin{equation}
        f_*: \lcfa_X \xrightarrow{\quad} \lcfa_Y.
    \end{equation}
\end{proposition}

\begin{corollary}\label{cor:pushforward_for_lc}
    Let $f: M \xrightarrow{} N$ be a constructible bundle of stratified manifolds. Then the pushforward functor for factorization homology of \Cref{prop:fh_pushforward} serves as a pushforward
    %
    \begin{equation}
        f_*: \lcfa_M \xrightarrow{\quad} \lcfa_N,
    \end{equation}
    %
    by using \Cref{thm:disk_alg=lcfa}.
\end{corollary}

\begin{remark}\label{rem:fh_is_pushingforward}
    Having defined the pushforward functor of factorization algebras we can consider the map $\mathsf{p}:M \rightarrow *$. Given any $A \in \alg{\disk(\bstr)_{/M}}$ the factorization algebra $F_A$ generated by $A$ satisfies
    %
    \begin{equation}
        \int_M A  = F_A(M) \simeq (\mathsf{p}_* F_A)(*).
    \end{equation}
    %
    The one point manifold is a very simple space, which makes the concepts of prefactorization algebras, factorization algebras and locally constant factorization algebras coincide. All of them are in fact given by a pointed object of the target category. Evaluation at $*$ simply returns the underlying object. Thus, in a sense evaluating factorization homology on a space $M$ is the same procedure as pushing-forward by the map $\mathsf{p}$. Versions of factorization homology that can evaluate lower dimensional manifolds (as compared to the structure of the disk algebra), for example as in \cite[cor.2.29]{aft_fhstrat}, can then be seen as relaxing this pushforward from $*$ to a manifold with more structure.
\end{remark} 

\begin{lemma}\label{lem:ff_functor_to_refinement}
    Let $u: X \rightarrow \hat{X}$ be the morphism that forgets the stratification. The functor $u_*: \lcfa_{X} (\catC) \rightarrow \lcfa_{\hat{X}} (\catC)$ has a fully faithful left adjoint.
\end{lemma}

\begin{proof}
    Consider the functor $\hat{-}: \falg_{\hat{X}} \rightarrow \falg_{X}$, which acts as $\hat{F}(U) := F(u(U))$, namely it returns algebras that evaluate open subsets by forgetting their stratification first. We claim this functor is the left adjoint of $u_*$. Indeed, given a morphism $(\phi: \hat{F} \rightarrow G) \in \falg_{X}$, i.e. a family of morphisms $\phi(U): \hat{F}(U) \rightarrow G(U)$ for all opens $U$ in $X$, it is easy to verify that we can construct a morphism of algebras over $\hat{X}$, $\hat{\phi}(u(U)): F(u(U)) \rightarrow u_*G (u(U))$, since $\hat{F}(U) = F(u(U))$ and $u_*G(u(U)) = G(u^{-1}(u(U))) = G(U)$. The last equality holds because $u$ is an injective map. In fact, this last observation also proves that the unit of this adjunction is an isomorphism, granting the full faithfulness.
\end{proof}

\begin{remark}
    In fact, the above proof is true more generally for any map of stratified spaces that is a homeomorphism of the underlying topological spaces (so, in particular, any refinement). This means that locally constant factorization algebras record the data of coarser stratified structures as $\infty$-subcategories. Forgetting local constancy, the proof, of course, applies to factorization algebras of all flavors, however for the types that don't detect the stratified structure the above functor is even an equivalence, and not just fully-faithful, and is of no interest.
\end{remark}


In the opposite direction, we do not, in general, have a pullback functor. \Cite{cg2016} provide a construction of a pullback in the case of open immersions, but we will only focus on the case of restrictions. Namely, given an open subset $U \subset X$ of a topological space $X$, and given a factorization algebra $F \in \falg_X$ we can clearly define a factorization algebra $F|_{U} \in \falg_U$ by restricting to those open subsets that are fully contained in $U$, which gives a functor
%
\begin{equation}
    \falg_X (\catC) \xrightarrow{\ \ -|_U \ \ } \falg_U (\catC).
\end{equation}
%
Furthermore, this clearly holds not only for factorization algebras, but prefactorization algebras and locally constant factorization algebras too.

In the special case of product spaces $X \times Y$, we now know that the projections $\pi_1: X \times Y \rightarrow X$ and $\pi_2: X \times Y \rightarrow Y$, give us pushforwards. For $\pi_1$, for example, this essentially uses the fact that if we can evaluate all open sets of $X \times Y$ then we can definitely evaluate the open sets that look like $U \times Y$, with $U \subset X$ an open set. But in this case we can do even more, because we can even evaluate the more granular open subsets $U \times V$ with $U \subset X$ and $V \subset Y$ opens. More formally, we claim:
%
\begin{proposition}\label{prop:exp_of_products}
    Let $X$ and $Y$ be topological spaces. There is a functor from the $\infty$-category of prefactorization algebras on the product $X \times Y$ to the $\infty$-category of prefactorization algebras on $X$ valued in the category of prefactorization algebras on $Y$
    %
    \begin{equation}
        \bar{\pi}: \alg{\opens(X \times Y)}(\catC) \xrightarrow{\qquad} \alg{\opens(X)} (\alg{\opens(Y)} (\catC)).
    \end{equation}
    %
    This functor descends to factorization algebras too
    %
    \begin{equation}
        \bar{\pi}: \falg_{X \times Y}(\catC) \xrightarrow{\qquad} \falg_{X}(\falg_{Y}(\catC)).
    \end{equation}
\end{proposition}

\begin{proof}
    Indeed, given opens $U \subset X$ and $V \subset Y$, the values we assign are $(\bar{\pi}F) (U)(V) = F(U \times V)$. Fixing an open subset $U \subset X$, we obviously get a prefactorization algebra $(\pi_2|_U)_* (F|_U) \in \alg{\opens(Y)}$ by pushing forward with $\pi_2|_U: U \times Y \rightarrow Y$, which shows that $\bar{\pi}F$ is valued in $\alg{\opens(Y)}$. The only thing left to show is that $\bar{\pi} F$ has the structure of a prefactorization algebra on $X$. To do this, for each multi-morphism $(\{ U_i \}_{i \in I} \rightarrow U) \in \opens(X)$ we assign a map $\bar{\pi}F (\{ U_i \}_{i \in I}, U)$ of factorization algebras on $Y$. Such an algebra map is specified by giving its value on all opens of $Y$ separately. We can thus assign
    %
    \begin{equation}
        \bar{\pi}F (\{ U_i \}_{i \in I}, U)(V) = F(\{ U_i \times V \}_{i \in I}, U \times V),
    \end{equation}
    %
    which uses the projections $\pi_1|_V : X \times V \rightarrow X$ to assign $\pi_1|_V^{-1}(U) = U \times V$.

    It is not hard to check that the above also holds for the example of factorization algebras on topological spaces, by using the result of \cite[ch.7.2]{cg2016}. However, we'll focus on manifolds, in which case, the construction from above immediately works since we now have to do it for $\disk[r]_{/X}$ instead of $\mfld[r]_{/X}$. The only things to mention is that products of disks are again disks \cite[cor.3.4.9]{aft_localstrut}.
\end{proof}


\begin{proposition}\label{prop:exp_of_products_lc}
    Let $M$ and $N$ be stratified manifolds. The functor $\bar{\pi}$ descends to locally constant factorization algebras, and moreover, it is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)).
    \end{equation}
\end{proposition}

\begin{remark}
    The above proposition also appears as \cite[prop.18]{ginot2015}. The equivalence proven there is for the case of smooth manifolds and relies on the local proof of \cite{lurie_ha} for $\mathbb{R}^n$. Using \Cref{thm:disk_alg=lcfa}, the statement is implied by the fact that there is an equivalence of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N},
    \end{equation}
    %
    with the tensor product of $\infty$-opeards. Again for smooth manifolds this is found in \cite[ex.5.4.5.5]{lurie_ha}.
\end{remark}

\begin{proof}
    The proof of existence of the functor goes along the same lines as the proof of \Cref{prop:exp_of_products} because of \Cref{thm:disk_alg=lcfa}. The thing to take into account is that the projection maps are both, trivially, constructible bundles so by \Cref{cor:pushforward_for_lc}, pushing forward by them yields locally constant factorization algebras again. This combined with the fact that for any $\infty$-operads $\mathscr{O}$, $\mathscr{O}'$ and $\mathscr{C}$ we have an equivalence
    %
    \begin{equation}
        \alg{\mathscr{O}} (\alg{\mathscr{O}'} (\catC)) \simeq \alg{\mathscr{O}'} (\alg{\mathscr{O}} (\catC))
    \end{equation}
    %
    allows us to conclude that the functor lands in locally constant factorization algebras
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{X \times Y}(\catC) \xrightarrow{\ \ \ \ } \lcfa_{X}(\lcfa_{Y}(\catC)).
    \end{equation}

    One way to show the equivalence is to use factorization homology, as in \Cref{thm:disk_alg=lcfa}, to write a locally constant factorization algebra as $\int_{-} A \in \lcfa_{X \times Y} (\catC)$. Then using the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \Cref{rem:fh_is_pushingforward}).} for factorization homology we get essential surjectivity because there are equivalences
    %
    \begin{equation}
        \int_{U \times V} A \xrightarrow{\ \ \simeq \ \ } \int_U \int_V \bar{\pi} A
    \end{equation}
    %
    between objects of $\catC$. As argued in the proof of \Cref{thm:disk_alg=lcfa}, these equivalences are natural in the open set variables, which means that they rise to equivalences at the level of locally constant factorization algebras. In fact, looking at the proof of \cite[thm.2.25]{aft_fhstrat}, which is what underlies the construction of the above equivalences, we see that they arise from an argument about a final functor. By \Cref{rem:fin_equiv_natural} this means that the equivalences are actually natural in the algebra variable, so it is immediate that the equivalences of individual locally constant factorization algebras lift to a full equivalence of $\infty$-categories.
\end{proof}




\subsection{Factorization Algebras on Intervals}\label{ssec:lcfa_on_ints}

We now turn to a few very important constructions of locally constant factorization algebras on intervals. Namely, we will consider how we can construct a locally constant factorization algebra on the spaces $\mathbb{R}$ (a.k.a. the open interval) and $\hoint$ (a.k.a. the half-open interval). These will be a very important backbone for intuition about locally constant factorization algebras, as well as a key part of proofs later on. We finish with factorization algebras for the closed interval $[-1,1]$.

\begin{construction}\label{con:lcfas_on_R}
    Consider a unital, (homotopy) associative algebra $A$ in the category $\catC$. We take the opportunity to construct a factorization algebra out of this data by hand. This is a feasible task since any open is some disjoint union of intervals. Thus, given any disk $U$ we assign the same value, $F_A(U) := A$. Similarly, given a multi-morphism $\sqcup_{i \in I} U_i \xhookrightarrow{} U$, with $I$ non-empty, we assign the map given by the multiplication of $A$
    %
    \begin{equation}
        F_A(\sqcup_{i \in I} U_i \xhookrightarrow{} U) := \otimes_{i \in I} A \rightarrow A.
    \end{equation}
    %
    The implicit convention, is that the ordering of the intervals, provided by the standard orientation (or framing) of $\mathbb{R}$, determines the order in which we multiply. Associativity forbids any other ordering except the completely opposite one, which would yield the opposite multiplication, and thus the opposite algebra. Finally, in the case of $\emptyset \xhookrightarrow{} U$, we assign the map that chooses the unit $\mathbb{1} \rightarrow A$. At this point we have constructed a prefactorization algebra on $\mathbb{R}$. Next we need to check the Weiss cosheaf condition. Because intervals are closed under finite intersections the \v{C}ech nerve definition of \Cref{rem:cech_nerve} makes this easy; the simplicial object $\cech_{\bullet}(\disk[r]_{/\mathbb{R}}, F_A)$ in all degrees will be a coproduct of copies of $A$. Thus, $F_A$ is indeed a factorization algebra. From the definition, it is also obviously locally constant.

    In this simple case the disks are closed under finite intersections, so the construction works out. More generally, one would need to find another factorizing basis. In the case of smooth manifolds one possible way is to choose a Riemannian metric and take the geodesically convex neighborhoods. An alternative is to get rid of the property of being closed under finite intersections altogether. It turns out, because of \Cref{thm:disk_alg=lcfa}, that this is indeed possible, and that we can always stick to using disks even in the most general situations.

    In whatever way we go about it, it is immediate that we have constructed a functor $\alg{\mathbb{E}_1}(\catC) \rightarrow \lcfa_{\mathbb{R}} (\catC)$ from the $\infty$-category of unital, (homotopy) associative algebras, or $\mathbb{E}_1$-algebras to the $\infty$-category of locally constant factorization algebras on $\mathbb{R}$. In fact, we claim that this functor is actually an equivalence, i.e., that every locally constant factorization algebra on $\mathbb{R}$ is equivalent to one induced like in the construction.
\end{construction}

\begin{proposition}\label{prop:R_gives_E1}
    There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\mathbb{E}_1}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}} (\catC).
    \end{equation}
\end{proposition}

\begin{proof}
    What is left to show is the essential surjectivity of the functor. This holds because every disk in $\mathbb{R}$ is diffeomorphic to $\mathbb{R}$ itself. So, given $F \in \lcfa_{\mathbb{R}}$, we can get an underlying object for our $\mathbb{E}_1$-algebra as $A = F(\mathbb{R})$. The previous observation and the local constancy then force the value on each disk to be equivalent to this. The space of embeddings of two disks $\mathbb{R} \sqcup \mathbb{R} \xhookrightarrow{} \mathbb{R}$ is, up to homotopy, equivalent to two points, which provide exactly the multiplication map $ A \otimes A \rightarrow A$ of the algebra and its opposite multiplication.  Associativity, up to homotopy, comes about exactly because all embeddings of any number of disks can, up to homotopy, be factorized through the embedding of two disks at a time. As before, the unit comes from the map $F(\emptyset \xhookrightarrow{} \mathbb{R}) = (\mathbb{1} \rightarrow A)$.
\end{proof}

\begin{construction}\label{con:lcfas_on_hoint}
    Consider a unital, (homotopy) associative algebra $A$ in the category $\catC$, as above, together with a unital right module $M$ of $A$ in the category $\catC$. From this data we will construct a locally constant factorization algebra $F_{(M, A)}$ on the stratified space $\hoint$. Considering \Cref{con:lcfas_on_R} and the open embedding $\mathbb{R} \cong \mathbb{R}_{>0} \xhookrightarrow{} \hoint$, we will choose the restriction to be $F_{(M,A)}|_{\mathbb{R}} = F_A$, i.e. any disk that doesn't include the point $0 \in \hoint$, we regard as a disk of $\mathbb{R}$ through the given map, and we assign the value $A$ to it like in the \Cref{con:lcfas_on_R}. This leaves us only with the stratified disks $U_*$ that contain the point $0 \in \hoint$. To these we assign the module $F_{(M,A)}(U_*) = M$. Since there can be at most one stratified disk that includes the point $0 \in \hoint$, the maps that we have to assign values to look like $U_* \sqcup (\sqcup_{i \in I} U_i) \xhookrightarrow{} U'_*$, but this is exactly what is provided by the right module structure
    %
    \begin{equation}
        F_{(M,A)} (U_* \sqcup (\sqcup_{i \in I} U_i) \xhookrightarrow{} U'_*) = M \otimes (\otimes_{i \in I} A) \rightarrow M.
    \end{equation}
    %
    Of course the pointing of the module comes from $F_{(M,A)}(\emptyset \xhookrightarrow{} U_*) = \mathbb{1} \rightarrow M$. As before, even more is true:
\end{construction}

\begin{proposition}\label{prop:hoint_gives_modules}
    There is an equivalence of $\infty$-categories between the $\infty$-categories of $\mathbb{E}_1$-algebras together with a right module and locally constant factorization algebras on the half-open interval
    %
    \begin{equation}
        \mathsf{RMod}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\hoint} (\catC).
    \end{equation}
\end{proposition}

\begin{proof}
    The proof goes along the same lines as the proof of \Cref{prop:R_gives_E1}. We can find the module by evaluating on $\hoint$, and we can find the algebra by evaluating on $\hoint \setminus \{ 0 \} \cong \mathbb{R}$, as a specified stratum of $\hoint$.
\end{proof}

\begin{remark}\label{rem:left_or_right_module}
    The fact that we chose left modules to provide the data in \Cref{prop:hoint_gives_modules}, does not play much of a role because a left module is exactly a right module of the opposite algebra, giving $\mathsf{LMod}(\catC) \simeq \mathsf{RMod}(\catC)$. Where the distinction comes up, is if we want to fix the $\mathbb{E}_1$-algebra away from $0 \in \hoint$ beforehand. In that case we have to use one of the two possible conventions on the order of multiplication. If we choose the increasing convention then the subset containing $0 \in \hoint$ is on the left making it a right module, while with the opposite convention it would be a left module of the opposite algebra.
\end{remark}

It's not hard to extend \Cref{con:lcfas_on_R} and \Cref{con:lcfas_on_hoint} to the closed interval $[-1,1]$ by hand, but through \Cref{thm:disk_alg=lcfa} we can see that \cite[cor.2.33]{aft_fhstrat} already do all the necessary work.

\begin{corollary}\label{cor:lcfas_on_closed_int}
    There is an equivalence between the $\infty$-categories of locally constant factorization algebras on the closed interval and algebras over the $\infty$-operad $\mathsf{Assoc^{RL}}$
    %
    \begin{equation}
        \lcfa_{[-1,1]} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathsf{Assoc^{RL}}} (\catC).
    \end{equation}
\end{corollary}

\begin{remark}
    Another perspective on why all of these constructions look the way they do is provided by \Cref{lem:disk/M_to_disk}. It applies in all of the above cases, namely:
    %
    \begin{enumerate}
        \item For $\mathbb{R}$, the convenient $\infty$-category of basics is $\bstr = \mathsf{D}_1^*$,
        \item For $[-1,1]$ the convenient $\infty$-category of basics is $\bstr = \mathsf{D}_1^{\partial, *}$.
        \item For $\hoint$, we could define a convenient $\infty$-category of basics which describes framed 1-dimensional manifolds which only have a right boundary (a concept that we can state because of the framing).
    \end{enumerate}
    %
    We can see that even though factorization algebras, as we have defined them here, don't detect the tangential structure of the manifold, it is usually favorable, if possible, to give the manifold some structure anyway. In particular, the rigid structure of framing is very useful because it massively reduces the spaces of allowed open embeddings.
\end{remark}


\subsection{Factorization Algebras on Euclidean Spaces}\label{ssec:lcfa_on_Rn}

\begin{theorem}[{\cite[thm.5.5.4.10]{lurie_ha}}]
    There is an equivalence of $\infty$-categories between the $\infty$-categories of locally constant factorization algebras on $\mathbb{R}^n$ and $\mathbb{E}_n$-algebras
    %
    \begin{equation}
        \alg{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n} (\catC).
    \end{equation}
\end{theorem}

\begin{proof}
    Since $\mathbb{R}^n$ is frameable, we can choose the $\infty$-category of basics $\mathsf{D}_n^* \simeq * \xrightarrow{\{ \mathbb{R}^n\}} \bsc$, and use \Cref{lem:disk/M_to_disk} to simplify the question; This makes us focus on framed $n$-dimensional disk algebras
    %
    \begin{equation}
        \lcfa_{\mathbb{R}^n} (\catC) \simeq \alg{\disk (\mathsf{D}_n^*)} (\catC).
    \end{equation}
    %
    With this, it is sufficient to show that there is an equivalence of $\infty$-operads
    %
    \begin{equation}
        \disk (\mathsf{D}_n^*) \xrightarrow{\ \ \simeq \ \ } \mathbb{E}_n.
    \end{equation}
    %
    But this is just the classical fact, that the little $n$-disks operad and the little $n$-cubes operad are equivalent, in disguise. One account of this fact with our terminology is, for example, \cite[prop.2.12]{aft_fhstrat}.
\end{proof}



\begin{remark}[{\cite[prop.3.16]{francis2013}, \cite[ex.5.5.4.16]{lurie_ha}}]
    In the case of Euclidean spaces like $\mathbb{R}^n$, essentially because of translation invariance, a special thing happens when we restrict away from the origin. That is, we know that given a locally constant factorization algebra $F$ on $\mathbb{R}^n$ we can restrict it to any open subset like, for example, $\mathbb{R}^n \setminus \{ 0 \} \cong S^{n-1} \times \mathbb{R}$ to get another locally constant factorization algebra $F|_{S^{n-1} \times \mathbb{R}}$. By \Cref{prop:exp_of_products_lc} we know that $F|_{S^{n-1} \times \mathbb{R}} \in \lcfa_{\mathbb{R}} (\lcfa_{S^{n-1}} (\catC))$, so that in particular it is an $\mathbb{E}_1$-algebra. If we pushforward to $\mathbb{R}$, by the discussion at \Cref{rem:fh_is_pushingforward} we could denote the resulting $\mathbb{E}_1$-algebra by
    %
    \begin{equation}
        \int_{S^{n-1}} F.
    \end{equation}
    %
    What \cite[prop.3.16]{francis2013} shows is then:

    \begin{proposition}\label{univ_env_for_En}
        Given a locally constant factorization algebra $F$ on $\mathbb{R}^n$, its universal enveloping algebra is given by $\int_{S^{n-1}} F$, i.e. there is an equivalence of $\infty$-categories
        %
        \begin{equation}
            \mathsf{Mod}^{\mathbb{E}_n}_{F} (\catC) \xrightarrow{\ \ \simeq \ \ } \mathsf{LMod}_{\int_{S^{n-1}} F} (\catC).
        \end{equation}
    \end{proposition}
    %
    This result goes towards an explanation of the appearance of factorization homology over higher spheres in the classification statement of \cite[prop.4.8]{aft_fhstrat}.
\end{remark}

We can view a Euclidean space $\mathbb{R}^{m+n}$ as a product space $\mathbb{R}^m \times \mathbb{R}^n$, in which case \Cref{prop:exp_of_products_lc} specializes to give the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}:

\begin{proposition}\label{prop:dunn_additivity}
    There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\mathbb{E}_{n + m}} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n} (\alg{\mathbb{E}_m} (\catC)). 
    \end{equation}
\end{proposition}

\begin{remark}
    The proof of \Cref{prop:exp_of_products_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented above and the one in \cite{lurie_ha} are independent. 
\end{remark}



% Generate bibliography
\newpage
\printbibliography

\end{document}
 
