\documentclass[../text]{subfiles} 

\begin{document}


\section{Collar-gluings and Disk Algebras}\label{ch:gluing_disk_alg}

Given a stratified manifold $M$, we defined the $\infty$-category of locally constant factorization algebras on it $\lcfa_M (\catC)$. We want to examine what we can say about the behavior of this $\infty$-category under collar-gluings in the manifold variable. Our discussion will be in terms of disk algebras $\alg{\disk_{/M}} (\catC)$, but using \cref{thm:disk_alg=lcfa} there is no loss at all.

\subsection{The Gluing Theorem}

\begin{theorem}\label{thm:gluing_alg_disk/M}
    Given a collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$, the $\infty$-category of $\disk_{/M}$-algebras is equivalent to the pullback of $\infty$-categories
    %
    \begin{equation}
        \alg{\disk_{/M}} (\catC) \simeq \alg{\disk_{/M_-}} (\catC) \bigtimes_{\alg{\disk_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\disk_{/M_+}} (\catC).
    \end{equation}
\end{theorem}

Before me move on to the proof we show a few useful lemmas.

\begin{lemma}\label{lem:fbar_func}
    A collar-gluing $f:M \xrightarrow{} [-1,1]$ of a stratified manifold $M$ induces a functor
    %
    \begin{equation}
        \bar{f}: \mfld_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld_{/M}),
    \end{equation}
    %
    which on objects acts as $(N \xhookrightarrow{} M) \mapsto (N_- \xhookrightarrow{} M, N_0 \times \mathbb{R} \xhookrightarrow{} M, N_+ \xhookrightarrow{} M)$. Moreover, this functor is even an algebra.
\end{lemma}

\begin{proof}
    Let us first look at the case of $\mfld[r]_{/M}$ instead of $\mfld_{/M}$. In this case the underlying $\infty$-category is actually (the nerve of) an ordinary category. In particular, morphisms are given by the data of an embedding $N \xhookrightarrow{} N'$ such that $N \xhookrightarrow{} N' \xhookrightarrow{} M = N \xhookrightarrow{} M$ on the nose.
    
    A collar-gluing of $M$ restricts to a collar-gluing of any $N$ that has an embedding into $M$ like the objects of our category. On the right-hand side, at the level of objects, the associative algebra structure is provided by embeddings that differ in the $\mathbb{R}$ factor and the module maps are provided by embeddings of the middle $N_0 \times \mathbb{R}$ into $N_-$ and $N_+$. At the level of morphisms we send the morphism $e: N \xhookrightarrow{} N'$ to
    %
    \begin{equation}
        (e_-: N_- \xhookrightarrow{} N'_-, \ e_0: N_0 \times \mathbb{R} \xhookrightarrow{} N'_0 \times \mathbb{R}, \ e_+: N_+ \xhookrightarrow{} N'_+).
    \end{equation}
    %
    The existence of these maps can be stated as the existence of a unique factorization, as in e.g.
    %
    \begin{equation}
        \begin{tikzcd}
            N_- \arrow[r, hook] \arrow[rd, dashed, hook, "e_-"'] & N \arrow[r, hook, "e"] & N', \\
            & N'_- \arrow[ru, hook] &
            \end{tikzcd}
    \end{equation}
    %
    where the diagram commutes on the nose. This also points out the difficulties that we will have to deal with in the case of $\mfld_{/M}$ concerning the higher morphisms.

    Sticking to $\mfld[r]_{/M}$ though, the assignment clearly plays well with the algebra structure of the right-hand side, through the existence of (on the nose) commutative diagrams like e.g.
    %
    \begin{equation}
        \begin{tikzcd}
            N_0 \times \mathbb{R} \arrow[r, hook, "e_0"] \arrow[d, hook] & N'_0 \times \mathbb{R} \arrow[d, hook]\\
            N_- \arrow[r, hook, "e_-"] & N'_-,
            \end{tikzcd}
    \end{equation}
    %
    so that we clearly get a functor
    %
    \begin{equation}
        \bar{f}: \mfld[r]_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld[r]_{/M}).
    \end{equation}

    Need to be extended to $\mfld_{/M}$ by dealing with the homotopies.

    %Formally, the relevant definition is \cite[def.2.1.2.7]{lurie_ha}, which says that we have to check two things: that the constructed functor $\gamma(A_-, A_+)$ lies over $\mathsf{Fin}_*$ and that it sends inert morphisms to inert morphisms. Factorization homology, $\int_- A_{0,\pm}$, satisfies this almost by definition, while \cref{lem:B_sym_mon} tells us that the bar construction similarly does so. All that is left to show is that $\bar{f}$ is a map of $\infty$-operads. But this is obviously the case since all it is doing is splitting the input into pieces while keeping track of how they relate to each other.
\end{proof}

\begin{corollary}\label{cor:fbar_func_discrete}
    Taking only the first part of the proof of \cref{lem:fbar_func} it is immediate that in the setting of $\mfld[r]_{/M}$ there is also a functor
    %
    \begin{equation}
        \bar{f}: \mfld[r]_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld[r]_{/M}),
    \end{equation}
    %
    that is an algebra.
\end{corollary}

\begin{lemma}\label{lem:B_sym_mon}
    The bar construction $\mathsf{B}: \alg{\mathsf{Assoc^{RL}}} (\catC) \xrightarrow{\ \ } \catC$ is a symmetric monoidal functor.
\end{lemma}

\begin{proof}
    The symmetric monoidal structure of $\alg{\mathsf{Assoc^{RL}}} (\catC)$ is inherited from $\catC$ pointwise. We denote the objects of $\alg{\mathsf{Assoc^{RL}}} (\catC)$ as $(R,A,L)$, and use $\mathsf{B}_{\bullet} (R, A, L):\Delta^{\mathsf{op}} \rightarrow \catC$ for the simplicial object of the bar construction. Using the language of \cite[def.2.1.2.7]{lurie_ha}, to prove that $\mathsf{B}$ is symmetric monoidal amounts to showing that for each basepoint-preserving map of based finite sets $f: I_* \xrightarrow{} J_*$ there is a commutative diagram of $\infty$-categories
    %
    \begin{equation}
        \begin{tikzcd}
            \alg{\mathsf{Assoc^{RL}}} (\catC)^I \arrow[r, "\mathsf{B}^I"] \arrow[d, "f_*"] & \catC^I \arrow[d, "f_*"] \\
            \alg{\mathsf{Assoc^{RL}}} (\catC)^J \arrow[r, "\mathsf{B}^J"] & \catC^J.
        \end{tikzcd}
    \end{equation}
    
    Following \cite[rem.2.1.2.2]{lurie_ha}, each $f$ admits a unique factorization as a composition of an active and an inert map. We can also further uniquely decompose the active maps into surjective active maps and injective active maps. So we will examine the above for each type of map separately. The case of inert maps is trivial as always, because of the simplicity of $f_*$. The case of injective active maps is essentially guaranteeing that $\mathsf{B}$ maps the monoidal unit to the monoidal unit. In this case the existence of the commutative diagram is provided by
    %
    \begin{equation}
        \mathsf{B} (\mathbb{1}_{\alg{\mathsf{Assoc^{RL}}} (\catC)}) = \mathsf{colim} (\mathsf{B}_{\bullet} (\mathbb{1},\mathbb{1},\mathbb{1})) \simeq \mathsf{colim} (\Delta^{\mathsf{op}} \xrightarrow{\{ \mathbb{1}\}} \catC) \simeq \mathbb{1}.
    \end{equation}
    %
    Finally, the case of surjective active morphisms describes what happens when we use the monoidal product to multiply. In this case we will look at the model calculation for the active map $f: \langle 2 \rangle \xrightarrow{} \langle 1 \rangle$. All other possibilities go along similar lines. Given two objects $H = (R,A,L)$ and $H' = (R',A',L')$ we have 
    %
    \begin{align}
        \mathsf{B}(H \otimes H') &= \mathsf{colim} (\mathsf{B}_{\bullet} ((R,A,L) \otimes (R',A',L')))\notag\\
        &= \mathsf{colim} (\mathsf{B}_{\bullet} (R \otimes R', A \otimes A', L \otimes L'))\notag\\
        &\simeq \mathsf{colim} (\mathsf{B}_{\bullet} (R, A, L) \otimes \mathsf{B}_{\bullet} (R', A', L'))\notag\\
        &= \mathsf{colim} (\Delta^{\mathsf{op}} \rightarrow \Delta^{\mathsf{op}} \times \Delta^{\mathsf{op}} \xrightarrow{\mathsf{B}_{\bullet} (R, A, L) \otimes \mathsf{B}_{*} (R', A', L')} \catC)\notag\\
        &\simeq \mathsf{colim} (\Delta^{\mathsf{op}} \times \Delta^{\mathsf{op}} \xrightarrow{\mathsf{B}_{\bullet} (R, A, L) \otimes \mathsf{B}_{*} (R', A', L')} \catC)\notag\\
        &\simeq \mathsf{colim} (\mathsf{B}_{\bullet} (R, A, L)) \otimes \mathsf{colim} (\mathsf{B}_{*} (R', A', L'))\notag\\
        &= \mathsf{B}(H) \otimes \mathsf{B}(H'),
    \end{align}
    %
    where $\Delta^{\mathsf{op}} \rightarrow \Delta^{\mathsf{op}} \times \Delta^{\mathsf{op}}$ is the diagonal functor. The first equivalence comes from the symmetric monoidal structure of $\catC$ dues to reshuffling in the simplicial object. The second equivalence uses the finality of the diagonal functor which comes from the fact that $\Delta^{\mathsf{op}}$ is sifted. Finally, the third equivalence exists because the symmetric monoidal structure of $\catC$ commutes with (sifted) colimits.
\end{proof}

\begin{proof}[Proof of \cref{thm:gluing_alg_disk/M}]
    The data of a collar-gluing provides open embeddings $M_0 \times \mathbb{R} \xhookrightarrow{} M_-$ and $M_0 \times \mathbb{R} \xhookrightarrow{} M_+$, where $M_-$, $M_0$ and $M_+$ have the usual meanings as in \cref{def:collar-gluing}. This can be used to construct the cospan of restriction functors $\alg{\disk_{/M_-}} (\catC) \rightarrow \alg{\disk_{/M_0 \times \mathbb{R}}} (\catC) \leftarrow \alg{\disk_{/M_+}} (\catC)$. Using this data we can define the pullback $\infty$-category
    %
    \begin{equation}
        \mathscr{P} := \alg{\disk_{/M_-}} (\catC) \bigtimes_{\alg{\disk_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\disk_{/M_+}} (\catC).
    \end{equation}
    %
    The further open embeddings of $M_-$, $M_0 \times \mathbb{R}$ and $M_+$ into $M$ again give rise to restriction functors that form a commutative square
    %
    \begin{equation}
        \begin{tikzcd}
            \alg{\disk_{/M}} (\catC) \arrow[r] \arrow[d] & \alg{\disk_{/M_+}} (\catC) \arrow[d] \\
            \alg{\disk_{/M_-}} (\catC) \arrow[r] & \alg{\disk_{/M_0 \times \mathbb{R}}} (\catC),
        \end{tikzcd}
    \end{equation}
    %
    which, by the universal property of the pullback, gives us a canonical functor $\rho: \alg{\disk_{/M}} (\catC) \rightarrow \mathscr{P}$. Our job is to find an inverse to this functor.
    
    Consider the following construction. Given the data of an object $(A_-, A_+) \in \alg{\disk_{/M_-}} (\catC) \times \alg{\disk_{/M_+}} (\catC)$ such that $A_-|_{M_0 \times \mathbb{R}} = A_+|_{M_0 \times \mathbb{R}} = : A_0$ we want to construct a functor $A: \disk_{/M} \xrightarrow{} \catC$. We do this by relying on factorization homology and the bar construction. Given $(U \xhookrightarrow{} M) \in \disk_{/M}$ we define
    %
    \begin{equation}\label{eq:def_of_A_in_proof}
        A(U) := \int_{U_-} A_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A_0} \int_{U_+} A_+,
    \end{equation}
    %
    where $U_-$, $U_0$ and $U_+$ are defined through the inherited collar-gluing $U \xhookrightarrow{} M \xrightarrow{} [-1,1]$. Well-definition of the bar construction is provided if we have the appropriate left and right module structures on $\int_{U_-} A_-$ and $\int_{U_+} A_+$ over the associative algebra $\int_{U_0 \times \mathbb{R}} A_0$. Pushforward along the restrictions $f|_{U_-}: U_- \rightarrow \left[-1, 1\right)$ and $f|_{U_+}: U_+ \rightarrow \left(-1, 1\right]$, together with the properties of factorization homology provides these left and right module structures. Furthermore, the associative algebra object is exactly the appropriate one since consecutive restrictions commute on the nose. The above argument is essentially the statement that there is a functor
    %
    \begin{align}
        \gamma: \mathscr{P} \xrightarrow{\ \ \int \ \ } &\alg{\mfld_{/M_-}}(\catC) \bigtimes\limits_{\alg{\mfld_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\mfld_{/M_+}} (\catC)\notag\\ &\xrightarrow{\ - \circ \bar{f} \ } \mathsf{Fun}(\mfld_{/M}, \alg{\mathsf{Assoc^{RL}}} (\catC)) \xrightarrow{\ \mathsf{B} \circ - \ } \mathsf{Fun}(\mfld_{/M},\catC) \xrightarrow{\ } \mathsf{Fun}(\disk_{/M}, \catC),
    \end{align}
    %
    where $\bar{f}$ is the functor from \cref{lem:fbar_func}.

    Our first order of business is to show that $\gamma$ actually even lands in $\alg{\disk_{/M}} (\catC)$, and not just $\mathsf{Fun}(\disk_{/M}, \catC)$. Since we have expressed the construction $A = \gamma(A_-, A_+)$ functorially, we can see that $A$ will inherit the structure of an algebra from the fact that factorization homology and the bar construction are symmetric monoidal functors (see \cref{lem:B_sym_mon} for the latter), together with \cref{lem:fbar_func} that lends this property to $\bar{f}$. With that we have constructed a functor
    %
    \begin{equation}
        \gamma : \mathscr{P} \xrightarrow{\ \ \ \ } \alg{\disk_{/M}} (\catC).
    \end{equation}
    
    Or strategy will be to show that the pair of functors $\rho$ and $\gamma$ give rise to an equivalence by first checking that this is the case on maximal $\infty$-subgroupoids and subsequently that it is also so on morphism spaces. Towards the first goal we need to show that:
    %
    \begin{enumerate}
        \item $\rho( \gamma (A_-, A_+))$ reproduces $(A_-, A_+)$ up to equivalence, and
        \item $\gamma (\rho (A))$ reproduces $A$ up to equivalence.
    \end{enumerate}
    %
    We now check these in order. Checking (1) amounts to evaluating disks $U$ which are contained in only one of the pieces $M_-$, $M_0 \times \mathbb{R}$ and $M_+$. For the case of $U_0 \times \mathbb{R} = \emptyset = U_+$, we have
    %
    \begin{equation}
        A(U) = \int_{U} A_- \bigotimes\limits_{\mathbb{1}} \mathbb{1} \simeq A_- (U),
    \end{equation}
    %
    and similarly if $U_- = \emptyset = U_0 \times \mathbb{R}$. Alternatively, for the case of $U_- = U_0 \times \mathbb{R} = U_+$ we instead have
    %
    \begin{equation}
        A(U) = \int_U A_0 \bigotimes\limits_{\int_{U} A_0} \int_U A_0 \simeq A_0(U).
    \end{equation}
    %
    If $U$ is such that $U_+ = \emptyset$, but $U_0 \times \mathbb{R} \neq \emptyset$ then
    %
    \begin{equation}
        A(U) = \int_U A_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A_-} \mathbb{1} \simeq \int_U A_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A_-} \int_{\emptyset} A_- \simeq \int_{U} A_- = A_-(U),
    \end{equation}
    %
    where the last equivalence is provided by the collar-gluing property of factorization homology. This observation is also what confirms (2). Namely,
    %
    \begin{equation}
        \int_U A \simeq \int_{U_-} A \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A} \int_{U_+} A \simeq \int_{U_-} A_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A_0} \int_{U_+} A_+,
    \end{equation}
    %
    where the first equivalence comes from collar-gluing, while the second is a rewriting using the fact that restricting the algebra doesn't change the value of factorization homology it just changes what we can evaluate with it.

    Finally, we want to show that $\rho$ is fully faithful, i.e. we want to show that
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{Hom}_{\alg{\disk_{/M}} (\catC)}(A, B) \arrow[r, bend left=4, "\rho"] & \mathsf{Hom}_{\mathscr{P}}((A_-, A_+), (B_-, B_+)) \arrow[l, bend left=4, "\gamma"]
        \end{tikzcd}
    \end{equation}
    %
    represents an equivalence of spaces for each $A, B \in \alg{\disk_{/M}} (\catC)$. That is, we have to do similar computations as (1) and (2) above, but now on the level of morphisms. Nothing new happens in the calculations involving restrictions that don't involve multiple pieces, since their logic essentially only depends on the properties of the bar construction when restricting. In the rest of the calculations we crucially used the collar-gluing property of factorization homology. That this property continues to hold at the morphism level is a consequence of the fact that we made sure to elevate the statement of \cref{prop:barconst=intinterval} to the level of functors, together with the pushforward property which also holds functorially à la \cref{rem:fh_pushforward_functorial}. Namely, these provide equivalences of functors
    %
    \begin{equation}
        \int_U - \simeq \int_{[-1,1]} (f|_U)_* - \simeq \mathsf{B} \circ (f|_U)_* = \int_{U_-} (-)_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} (-)_0} \int_{U_+} (-)_+,
    \end{equation}
    %
    which is exactly the collar-gluing property extended to the level of morphisms.
\end{proof}

Together with \cref{thm:disk_alg=lcfa} we immediately have the following corollary:

\begin{corollary}\label{cor:gluing_lcfas}
    A collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$ induces an equivalence of $\infty$-categories
    %
    \begin{equation}
        \lcfa_M (\catC) \simeq \lcfa_{M_-} (\catC) \bigtimes_{\lcfa_{M_0 \times \mathbb{R}} (\catC)} \lcfa_{M_+}(\catC).
    \end{equation}
\end{corollary}

\begin{remark}
    The simple case when the collar-gluing is a disjoint union, and the manifolds are smooth can also be found as \cite[ex.5.4.5.4]{lurie_ha}.
\end{remark}

Taking into account \cref{cor:disk_alg=falg} together with \cref{cor:fbar_func_discrete}, as well as the definition of factorization homology in the setting of the category $\disk[r]_{/M}$, the proof of \cref{thm:gluing_alg_disk/M} can be seen to clearly hold even in case of ordinary factorization algebras.

\begin{corollary}\label{cor:gluing_falgs}
    A collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$ induces an equivalence of $\infty$-categories
    %
    \begin{equation}
        \falg_M (\catC) \simeq \falg_{M_-} (\catC) \bigtimes_{\falg_{M_0 \times \mathbb{R}} (\catC)} \falg_{M_+}(\catC).
    \end{equation}
\end{corollary}


\subsection{Some Examples of Gluing}

\begin{example}\label{ex:reproduce_lcfas_on_S1}
    Using results from \cite[prop.4.0.1]{cg2016}, namely inheritance from a covering space, \cite[sec.5.5]{ginot2015} characterizes locally constant factorization algebras on the circle $S^1$ as
    %
    \begin{equation}
        \lcfa_{S^1} (\catC) \simeq \aut (\alg{\mathbb{E}_1} (\catC)),
    \end{equation}
    %
    i.e. $\mathbb{E}_1$-algebras together with a self-equivalence. \Cref{cor:gluing_lcfas} allows us to recover this nontrivial result. To wit, the circle can be exhibited as a collar-gluing $S^1 \cong \mathbb{R} \coprod_{S^0 \times \mathbb{R}} \mathbb{R} \cong \mathbb{R} \coprod_{\mathbb{R} \sqcup \mathbb{R}} \mathbb{R}$. For locally constant factorization algebras this means that
    %
    \begin{equation}\label{eq:lcfas_on_S1_gluing}
        \lcfa_{S^1} (\catC) \simeq \lcfa_{\mathbb{R}} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \alg{\mathbb{E}_1} (\catC).
    \end{equation}
    %
    Since a disjoint union is a collar-gluing we also have that $\lcfa_{\mathbb{R} \sqcup \mathbb{R}} \simeq \lcfa_{\mathbb{R}} (\catC) \times \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \times \alg{\mathbb{E}_1} (\catC)$. Let's denote the restriction functors that restrict to the first and the second component of the disjoint union $\mathbb{R} \sqcup \mathbb{R}$ by $|_1$ and $|_2$ respectively. Going back to \cref{eq:lcfas_on_S1_gluing}, the data of a locally constant factorization algebra on $S^1$ is equivalent to the data of two $\mathbb{E}_1$-algebras $A$ and $B$ such that their restrictions $A|_1 = B|_1$ and $A|_2 = B|_2$ agree. Since all of these are $\mathbb{E}_1$-algebras there are equivalences with the restrictions forming
    %
    \begin{equation}
        \begin{tikzcd}[row sep = small, column sep= small]
            & A|_1 \arrow[r, phantom, "=", description] & B|_1 & \\
            A \arrow[rd, phantom, "\simeq", sloped, description] \arrow[ru, phantom, "\simeq", sloped, description] & & & B \arrow[lu, phantom, "\simeq", sloped, description] \arrow[ld,  phantom, "\simeq", sloped, description] \\
            & A|_2 \arrow[r, phantom, "=", description] & B|_2 &                        
        \end{tikzcd}
    \end{equation}
    %
    That is we have the data of two algebras $A$ and $B$, and two equivalences from $A$ to $B$. It is standard that this data is equivalent (in one direction by composing) to the data of an $\mathbb{E}_1$-algebra with a self-equivalence.
\end{example}

\begin{example}\label{ex:lcfas_on_S^n}
    Just as for the circle, higher spheres can also be described as a collar-gluing $S^n \cong \mathbb{R}^n \coprod_{S^{n-1} \times \mathbb{R}} \mathbb{R^n}$. Thus, we can iterate the procedure from \cref{ex:reproduce_lcfas_on_S1} to get the locally constant factorization algebras on all higher spheres. For example, for the two-sphere $S^2$ we have
    %
    \begin{equation}
        \lcfa_{\mathbb{R}^2}(\catC) \bigtimes_{\lcfa_{S^1 \times \mathbb{R}}(\catC)} \lcfa_{\mathbb{R}^2}(\catC) \simeq \alg{\mathbb{E}_2}(\catC) \bigtimes_{\alg{\mathbb{E}_1}( \aut (\alg{\mathbb{E}_1} (\catC))) } \alg{\mathbb{E}_2} (\catC),
    \end{equation}
    %
    namely, a locally constant factorization algebra on $S^2$ is equivalent to two $\mathbb{E}_2$-algebras, such that they restrict on the fattened equator to the same $\mathbb{E}_2$-algebra equipped with an $\mathbb{E}_1$-automorphism. It is nontrivial to describe this data in a simpler way as was possible for $S^1$.
    
    From this example we can easily see that beyond the dimensionality $n$ of the space, which is locally kept track of as an $\mathbb{E}_n$-algebra, locally constant factorization algebras for the higher spheres also keep track of higher coherent (self-)equivalences.
\end{example}

\begin{example}\label{ex:cylinder_mobius_band}
    In \cref{ch:classif_defect_mfld} we will see that fiber bundles are important for the classification of some stratified manifolds. Here we will look at line bundles over the circle as a toy example, namely, the cylinder $C$ and M\"obius band $M$. The cylinder, as a trivial fiber bundle, is isomorphic to the product space $S^1 \times \mathbb{R}$. By \cref{prop:exp_of_products_lc} together with the results of \cref{ex:reproduce_lcfas_on_S1}, locally constant factorization algebras on it are given by $\mathbb{E}_2$-algebras together with an $\mathbb{E}_1$-self-equivalence
    %
    \begin{align}
        \lcfa_C (\catC) \simeq \aut_{\mathbb{E}_1} (\alg{\mathbb{E}_2} (\catC)).
    \end{align}

    Switching our attention to the M\"obius band $M$, we can use a similar logic as in \cref{ex:reproduce_lcfas_on_S1} to find a collar gluing of $M$. The pieces are the same as they would be for the cylinder, namely $M_- \cong M_+ \cong \mathbb{R}^2$, and $M_0 \times \mathbb{R} \cong \mathbb{R}^2 \sqcup \mathbb{R}^2$, but they are glued differently because of the twist. Using the notation from \cref{ex:reproduce_lcfas_on_S1} the diagram becomes
    %
    \begin{equation}
        \begin{tikzcd}[row sep = small, column sep= small]
            & A|_1 \arrow[r, phantom, "=", description] & B|_1^{\mathsf{op_f}} \arrow[r, phantom, "\simeq", description] & B^{\mathsf{op_f}} \\
            A \arrow[ru, phantom, "\simeq", sloped, description] \arrow[rd, phantom, "\simeq", sloped, description] & & & \\
            & A|_2 \arrow[r, phantom, "=", description] & B|_2 \arrow[r, phantom, "\simeq", description] & B,
        \end{tikzcd}
    \end{equation}
    %
    where $^{\mathsf{op_f}}$ is the opposite functor in the fiber direction. Thus, instead of an $\mathbb{E}_1$-\emph{self}-equivalence we have an equivalence with the opposite algebra.

    We should remark that the fact that we can take the opposite algebra in one direction only is a consequence of the Dunn additivity of \cref{prop:dunn_additivity}. Without it, we wouldn't be able to combine the opposite algebra in one direction with the original algebra in the other direction into a well-defined algebra in two dimensions.
\end{example}

\end{document}